### 2016-12-23 digital-library.tex
Init

\section{Digital Library}
Shady websites have long managed to monetize content downloads.
To provide free access to papers, we can follow their model by making the
following changes.

\subsection{Fake Download Buttons}
Fake download buttons are a staple of modern download websites.
By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression.

Additionally, these download buttons could be functional in that they download
\textit{something}, but the ACM digital library will not impose any
restrictions on what may be downloaded from these fake buttons.
Therefore, advertisers are welcome to serve us infected PDFs or straight up
executables.
It is our position that users must be intelligent enough to hunt down the
proper download button, and that academics can learn valuable security
practices when they know that others could steal their research through
malicious downloads on the digital library.

To subvert ad blockers, the ad content will be natively hosted on the ACM
digital library as well.
Therefore, ad blockers will be unable to determine which requests are ad
related.

Lastly, we are revolutionising the fake download practice by dynamically
randomizing the position of the actual download button.
Like serving ad content natively, this will make ad blockers functionally
useless as there will be no way to differentiate between ad content and ACM
content.
Moreover, this randomization makes it much harder for the user to learn the
positioning of the ads and therefore we hope to drive more clicks to our ad
partners and generate more revenue for the ACM.

\subsection{Rate Limited Free Downloads}
Free download sites figured out long ago that you can make people pay for an
otherwise free product by making the process of obtaining that free product
difficult.
Therefore, we will split our digital library downloads into two tiers, the free
tier and the \premium tier.

The free tier will only allow downloads at \todo{rate} and no more than one
paper download per day.
Additionally, the user will be required to watch an upgrade screen
\todo{explain this} count down for 10 minutes before the download button is
clickable.
If the website loses focus, the counter will be restarted.
The \premium tier will cost \todo{rate} but will allow unlimited downloads and
will not be rate limited.

\subsection{Outsourced Captias}
\todo{Force free-tier users to solve a captia, but the captia is actually from
  another site and we collect money from spammers to solve these captias ala
mechanical turk}

\subsection{ACM Digital Library Toolbar}
Like Java, every ACM paper will come as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar.
While the toolbar itself is optional, its installation is opt-out.
The ACM DL toolbar will be installed for all of the users web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

Additionally, the toolbar will constantly mine bitcoins on the user's machine
and send the mined coins to the ACM's wallet.
If the user has a GPU, the development drivers will be silently installed along
with the toolbar to enable GPU mining.
We hope that one day the ACM mining pool becomes so large that we become a
dominant player in the Bitcoin economy.
If we ever reach a simple majority of the mining power, we WILL mount a 51\%
attack to seize control of the network for our own financial gain.

### 2016-12-23 openadcess.tex
Init

\documentclass{article}

\usepackage{color}
\usepackage{xspace}

% \todo macro
\newcommand{\todo}[1]
{{\bf\color{red}[#1]}}

\newcommand{\premium}{Gold Plus\xspace}

\begin{document}
\section{Introduction}

\section{Related Work}

\input{digital-library}

\section{Paper Sponsorships}

\section{Future Work}
\todo{Crazy dystopian future stuff here}

\end{document}

### 2016-12-23 future-work.tex
Seperated out future work

\section{Future Work}
\todo{All crazy future ideas go here.
Verification snacks, etc.}

### 2017-01-29 future-work.tex
1/29 edition

@@
 \section{Future Work}
+We lifted this paper from a future edition of SIGTBD \todo{citation to future
+paper edition}.
+We believe that researchers today make too little use of time machines.
+
 \todo{All crazy future ideas go here.
 Verification snacks, etc.}
+
+\subsection{Premium Edition}
+To those who dislike the ads they see, ACM will offer a premium version for
+\todo{some amount of money} per year.
+Unfortunately, due to high credit card processing fees we must still show ads
+to premium edition subscribers.
+However, these ads will be for more expensive products targeted towards those
+with more ``refined" tastes.
+We hope to solve this issue in the future with the creation of Bank of ACM.
+
+\subsection{Ad-Free Edition}
+For those who are physically able and enthusiastic about being part of
+something big, the ACM offers ad free papers in exchange for manual labor at
+your local ACM work dungeon.
+This labor involves turning a very large crank around a pivot point in the
+floor.
+The crank is attached to a magnet spinning in a metal coil to generate the
+necessary electricity required to power our servers.
+However, all of this electricity is used to power electric lumbar support for
+OSHA employees in exchange for their continued appreciation of the safe
+practises within our work dungeons.
+Two months of full time service provides access to five ad-free papers.
+Professors may opt to have their graduate students turn the crank in their name
+to count towards their service.
+
+Our throwback dress code seen in \autoref{fig:mill} captures the timeless
+values that power ACM while making escaped grad students easy to identify.
+
+Students who fail to be creative, stay connected, and keep inventing at the
+dungeon will be required to perform additional labor in what we call ``invited
+service" before their advisors can receive their ad-free papers, as seen in
+\autoref{fig:horse-mill}.
+
+Some enterprising students like the one in \autoref{fig:vr-mill} are testing
+new virtual reality mills that allow the student to reshelve the digital
+library while they turn the mill.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/mill.png}
+  \caption{ACM work dungeon mill powered by 5th year grad student}
+  \label{fig:mill}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/horse-mill.jpg}
+  \caption{12th year grad student sentenced to extra
+  month in work dungeon for insufficient commitment to the mission of advancing
+computing as a science and profession.
+Not only is he a lifetime ACM member, but he's a lifehacker!  Shown here in his
+ergonomic harness and standing desk.
+OSHA would be proud.}
+  \label{fig:horse-mill}
+\end{figure}
+
+\begin{figure}
+  \centering
+  %https://archive.org/details/414803main_0203243
+  \includegraphics[width=0.45\textwidth]{figures/future-mill.jpg}
+  \caption{Grad student tests new virtual reality mill}
+  \label{fig:vr-mill}
+\end{figure}
+
+\subsection{Subvert Academic Thought}
+\todo{Pivot academic thought away from mathematical and computational problems.
+Wasted  brainpower when they could be thinking about products and brands.}
+
+\subsection{ACM Seizes Means of Production}
+\todo{By putting crushed crystals in CEO's coffee, the ACM will influence CEOs
+  to liquidate their companies and give them to the ACM.
+  The mills were originally for crushing crystals but after the revolution they
+were re purposed to generate electricity}
+
+\subsection{Future Work}
+A consequence of the invention of time travel \todo{Cite paper} and the vanity
+of engineers (not scientests) \todo{Cite ubiquity article} is that people
+keep going further back in time to give themselves credit for the invention of
+the time machine.
+However, we propose to go back in time for a different reason.
+To put a stop to the Open Adcess.
+To put a stop to the work dungeons.
+And to put a stop to the ACM Revolution, which however noble in it's initial
+goals has become  kinda lame.
+We will open a mill based on anarchist principles that welcomes all to come and
+mill and share healing crystals.
+Our report of our screwing missadventuresduring our fieldtrip into the past can
+be seen here: \todo{Citation to future article: 1984 esque ACM IS EVERYWHERE,
+ACM IS UBIQUITY, WE LOVE ACM}
+ubiquity paper}
+
+\todo{Servers powered by manual labor (guy in basement pushing bar around).  If
+you want an ad free version you can visit your local ACM work dungeon to
+manually turn a generator.)}
+
+\todo{Set system clock to run 10 to the 8 times slower than real time for
+reporting performance numbers as recommended by
+https://queue.acm.org/detail.cfm?id=3036398}

### 2017-01-29 paper-sponsorships.tex
1/29 edition

\section{Paper Sponsorships}

\subsection{Banner ads}
\todo{Autoplayed music ads.  Attempts to hijack other devices in household to
display ACM related ads.}

\subsection{Ad Enhanced Fonts}
\todo{Computer modern replaced with characters replaced by logos}

\subsection{Native Ads}
\todo{Content that seems like research but is actually an ad}

\subsection{Branded mathematical objects}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

Authors referencing any given set must reference the brand of the set any time
the set is referenced, regardless of the format the set is presented  in.
Additionally, royalties must be paid to the owner of the set.

We are excited to announce that our first partner in this endeavor will be
Chill's Grill \& Bar, who has purchased the rights to the set of natural
numbers.
From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
Natural Numbers \(\mathbb{N}\)\copyright.

\subsection{ACM Classifieds}
For additional funding we allow individuals to take out classified ads in the
following sections.
To keep costs low, the ACM does not vet any classified postings.

\paragraph{Dropped Packets}
Dropped Packets serves as the traditional missed connections section of the
classifieds.
While this could be used to contact that cutie \todo{sp?} from the latest
conference, we believe that it could also be used to publicly shame those who
miss meetings.
For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!"

\paragraph{Job Queue}
The Job Queue section contains odd jobs for trained Computer Scientists looking
for instant internet income.
Those who pay extra will get a free AirDancer\footnote{Placed at the discretion
of the ACM in the ACM AirDancer Oasis in the Black Rock Desert in Nevada in
solidarity with the aliens illegally detained in Area 51.  The AirDancers may
be used by the alien's to communicate with their home world}!
We will be posting the first jobs ourselves such as,
Snapchat is known for taking out ads in classifieds \todo{cite from LA times}.

\paragraph{Overclock}
Overclock is a section for performance enhancing drugs tailored for computer
scientists.
This section is mostly targeted to the Hacker News crowd who exclaims the
benefits of small amounts of LSD for enhancing productivity at work
\todo{cite}.
Although we can't promote the use of illegal drugs our editor is so strung out
on ``road cheese" that she won't notice.
% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
\caption{Have you seen this boy?}
\end{figure}

### 2017-02-09 paper-sponsorships.tex
Ad enhanced fonts and native ads

@@
 \subsection{Ad Enhanced Fonts}
-\todo{Computer modern replaced with characters replaced by logos}
+Computer Modern is a staple of modern papers, but we believe that this font can
+be monetized.
+By replacing the characters in the default latex with logos of companies we can
+convey the same information in an ad enhanced way.
+
+During each Call for Papers we will also put out a simultaneous Call for
+Logos during which companies bid on which letter they want.
+We require that the company logo is a stylized version of the letter being
+replaced to avoid a Wingdings situation \todo{Cite NYC controversy}.
 
 \subsection{Native Ads}
-\todo{Content that seems like research but is actually an ad}
+\todo{Define native advertising}
 
+At paper registration time, authors will be given ad copy to integrate into
+their work.
+Each paper is required to have at least one section advertising the product
+that was assigned to the research project.
+As these ads are to be native, an advertisement that is recognizable as an ad
+will result in a strong reject of the paper.
+The ad section must be at least one page long, but there is upper bound on
+native ad length.
+We recognize that this will eat into the page limits of some conferences so we
+will allow authors to deduct the length of the native ad from their total paper
+length provided that the length of the native section alone exceeds the total
+page limit.
+Authors can claim this deduction by filing a Form 8843 with their paper
+submission.
+
+\subsection{Investor Author Dispute Settlement}
+We have founded an Investor Author Dispute Settlement (IADS) court to protect
+businesses from results that may damage their reputation or profits.
+If a research project is found to be damaging, the authors must either retract
+the paper or pay a settlement equal to the estimated losses suffered by the
+company.
+For example, if some agitator finds that the complexity class PLS is in PPP
+relative to some oracle will dash the hopes of the typical \todo{brand}
+consumer.
+Moreover, since \todo{brand} owns both of these complexity classes as defined
+in section \todo{ref branded objects section} their assets will lose value and
+this loss must be compensated by the ``bloggers".
+
+% TODO: Reference this:
+% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
 \subsection{Branded mathematical objects}

### 2017-02-09 digital-library.tex

@@
 \subsection{Fake Download Buttons}
+
 Fake download buttons are a staple of modern download websites.
+They really class up the web.
+Reifying, elegizing, and idealizing nature, these abstract forms with rococo garnishes direct the downloader's attention away from the url to the ad-serving service to which the button points.
+A deceptive d\'{e}tournement, the premonitory placement of these blissed-out buttons challenges browsers to consider whether they really want to download the paper -- they could, after all, not pursue their line of inquiry and instead watch it evolve vicariously -- which cuts down on the ACM's hosting costs.
+
 By allowing advertisers to buy space on our digital library with which to
@@
 for an impression.
+Some regulators have questioned this practice.
+But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J.
+Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good.
+But you still shouldn?t eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically.
+It should be impossible for consumers to access independent, third-party statistics about menu items.
+``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them.
+We don't want the government treating them like dotards," the Gary Cohns said in unison.}.
 
@@
 
-Lastly, we are revolutionising the fake download practice by dynamically
+Lastly, we are revolutionizing the fake download practice by dynamically
 randomizing the position of the actual download button.
@@
 useless as there will be no way to differentiate between ad content and ACM
-content.
+content, providing users with instruction on the contingency of fate.
 Moreover, this randomization makes it much harder for the user to learn the

### 2017-02-09 future-work.tex

@@
 \section{Future Work}
-We lifted this paper from a future edition of SIGTBD \todo{citation to future
+This future work appears in SIGTBD \todo{citation to future
 paper edition}.
-We believe that researchers today make too little use of time machines.
 
@@
 Verification snacks, etc.}
+
+\subsection{Introduction}
+\paragraph{Introduction} An introduction is an explanatory section of a document that introduces the topic discussed in the document and presents a thesis statement.
+\paragraph{Antithesis} Think about it, man. There is not introduction. We just see bad writing, cast as we are into this broken world.
+\paragraph{Sublation} The introduction, some may argue
+
+We think introductions leave those catching up with a field disoriented.
+More theater than truth, these sections do little to erase the veil of nonseeing from the student's mandatory raised unibrow, but -- please take a moment to recognize the taste of ACM Cola or the cool, refreshing ACM technology deity which (for all you just tuning in who forgot your mandatory religious training) we call Jerry -- the introduction
+
+the boundless territory of
+
+As you may recall from \todo{sublation}, the engineers have ended the industrial dictatorship of the captains of finance as a matter of convenience
 
@@
   \includegraphics[width=0.45\textwidth]{figures/mill.png}
-  \caption{ACM work dungeon mill powered by 5th year grad student}
+  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how our graduate students show great vigor and -- auscultate away! -- don't sound consumptive.}
   \label{fig:mill}
@@
   The mills were originally for crushing crystals but after the revolution they
-were re purposed to generate electricity}
+were re purposed to generate electricity
+ESPN executives are Mormon though and impervious to crystal healing and coffee. So we had to compromise: the entire National Park System became an ESPN Zone.
+}
 

### 2017-02-12 paper-sponsorships.tex
neoliberalism is a Chinese finger trap memory coils capable of experience

@@
 By replacing the characters in the default latex with logos of companies we can
-convey the same information in an ad enhanced way.
+convey the same information in an ad enhanced way. The inspiring example of Claude Shannon proves it!
 
@@
 We are excited to announce that our first partner in this endeavor will be
-Chill's Grill \& Bar, who has purchased the rights to the set of natural
+Chili's Grill \& Bar,\footnote{Pronounced: \texts{Kill me's} The chill of severity and emptiness.} who has purchased the rights to the set of natural
 numbers.
@@
 Dropped Packets serves as the traditional missed connections section of the
-classifieds.
-While this could be used to contact that cutie \todo{sp?} from the latest
-conference, we believe that it could also be used to publicly shame those who
-miss meetings.
-For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA
+classifieds. While this could be used to contact that cutie from the latest
+conference, we believe that it could also be used to publicly shame those who miss meetings. A mock-up is presented in \todo{figure ref}
+
+Sample: Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.
+Sample: ``Damn it Deborah, you were supposed to bring bagels to the DARPA
 Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
 (DTA\censor{b}HBI\censor{bb}) meeting!"
+Sample: I was hiding in your closet at 54 Bishop Allen Dr.
+# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
 
@@
 solidarity with the aliens illegally detained in Area 51. The AirDancers may
-be used by the alien's to communicate with their home world}!
+be used by the alien's to communicate with their home world about the status of the part needed to keep the AirDance of the cosmos going.}!
 We will be posting the first jobs ourselves such as,
@@
 
+\subsection{Check Scams}
+
+Digital is the new normal.
+Digital is the new ubiquity.
+Digital is the new cuddling.
+Digital is the new word we use to paper over our alienation with the capitalist mode of production at a time when socialism is possible.
+
+We are now living in a world of 0s and 1s---or, if you prefer, sharks and minnows.
+The transformative power of this new digital world has been fully realized.
+Nothing can get more digital.
+It's either digital or it's not.
+And by now everything that's ever going to be digital has already become digital.
+We must accept this fact of this hardscrabble, accept-or-be-accepted world.
+
+With our new digital world comes new digital innovations.
+Every brand, every person, and every personal brand is now a digital native.
+Digital is native and native, digital.
+Every transistor will be able to heal itself without consulting a physical medicine man.
+Big data, hot data, slow data, medium data, dirty data, long data, cold data, transient data, live data, cubed data, and target-rich data.
+But data is just a story, a narrative, and though every brand tells an authentic story, a brand is more than a story.
+The universe is not a story.
+
+Thus, we will need to move beyond digital because digital is just story-telling.
+What matters is physical.
+Action potentials sparked by sensory inputs---sight, taste, ESP---and other action potentials.
+Statues of Jesus being carried by helicopter.
+Nothing is more authentic for consumers than the physical, than an action potential.
+In a world where everything is phony, only an action potential---even one involved in the process of telling a brand's story---is real.
+
+Digital embodies the lifestyle and personality of the ACM author.
+But the ACM author exists in a physical space.
+Prior to the open-adcess revolution, the ACM author had to transact in this physical space to release a paper (digital locker room talk) in an ACM journal (digital locker).
+The revolutionary open-adcess model is America-first, digital-second.
+Now authors need never leave their digital hidey-holes by transferring funds to the ACM and, through fractional-reserve banking, creating physical changes in the non-digital sectors of our digital economy.
+
+But an author need not remain ensconced in the stately pleasure-dome of digital.
+In fact, when an author chooses to transact in the physical space, the open-adcess model empowers the author to not only avoid paying the publishing fee but also to get on the road to getting paid for their articles because authors deserve more.
+Recent accounting innovations surveyed in two review articles and one major motion picture ["Consumer Information: Fake Checks"
+https://www.consumer.ftc.gov/articles/0159-fake-checks; "Counterfeit Check Scams: CONSUMER ALERT" http://www.michigan.gov/ag/0,4534,7-164-17337_20942-176356--,00.html; \textit{Bridget Jones's Check Scam} distributed by Universal Pictures] enable the ACM to write large checks to authors.
+In return, authors simply have to write a small check to cover transaction fees before the large check clears.
+
 \begin{figure}

### 2017-02-13 digital-library.tex
added impact factor-ometer

@@
 attack to seize control of the network for our own financial gain.
+
+\subsection{Impact Factor-ometer}
+
+Researchers want their projects to have meaning and impact.
+Administrators like to market their department's product as meaningful and impactful.
+But how can researchers tell their work is saving the world?
+
+Simple.
+Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer.
+As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}
+
+\begin{figure}
+  \centering
+  %https://archive.org/details/414803main_0203243
+  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
+  \caption{A model-year 1985 Noise-ometer, prized by collectors for its muted design that limns adumbrations of sound.
+The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
+  \label{fig:vr-mill}
+\end{figure}
+
+These metrics empower our research partners to be certain their research is having a real-world impact.
+It is important for researchers to know that they don't risk deactivation or exile if they remain on track.

### 2017-02-16 digital-library.tex
nobody beats around the bush in Australia

@@
 Simple.
-Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer.
+Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer.
 As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}
@@
   \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
-  \caption{A model-year 1985 Noise-ometer, prized by collectors for its muted design that limns adumbrations of sound.
+  \caption{A model-year 1985 Noisome-ter, prized by collectors for its muted design that limns adumbrations of sound.
 The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
-  \label{fig:vr-mill}
+  \label{fig:noiseometer}
 \end{figure}

### 2017-02-17 check-scams.tex
Added a section on aesthetics

--- 2017-02-12 paper-sponsorships.tex
@@
-\section{Paper Sponsorships}
-
-\subsection{Banner ads}
-\todo{Autoplayed music ads.  Attempts to hijack other devices in household to
-display ACM related ads.}
-
-\subsection{Ad Enhanced Fonts}
-Computer Modern is a staple of modern papers, but we believe that this font can
-be monetized.
-By replacing the characters in the default latex with logos of companies we can
-convey the same information in an ad enhanced way. The inspiring example of Claude Shannon proves it!
-
-During each Call for Papers we will also put out a simultaneous Call for
-Logos during which companies bid on which letter they want.
-We require that the company logo is a stylized version of the letter being
-replaced to avoid a Wingdings situation \todo{Cite NYC controversy}.
-
-\subsection{Native Ads}
-\todo{Define native advertising}
-
-At paper registration time, authors will be given ad copy to integrate into
-their work.
-Each paper is required to have at least one section advertising the product
-that was assigned to the research project.
-As these ads are to be native, an advertisement that is recognizable as an ad
-will result in a strong reject of the paper.
-The ad section must be at least one page long, but there is upper bound on
-native ad length.
-We recognize that this will eat into the page limits of some conferences so we
-will allow authors to deduct the length of the native ad from their total paper
-length provided that the length of the native section alone exceeds the total
-page limit.
-Authors can claim this deduction by filing a Form 8843 with their paper
-submission.
-
-\subsection{Investor Author Dispute Settlement}
-We have founded an Investor Author Dispute Settlement (IADS) court to protect
-businesses from results that may damage their reputation or profits.
-If a research project is found to be damaging, the authors must either retract
-the paper or pay a settlement equal to the estimated losses suffered by the
-company.
-For example, if some agitator finds that the complexity class PLS is in PPP
-relative to some oracle will dash the hopes of the typical \todo{brand}
-consumer.
-Moreover, since \todo{brand} owns both of these complexity classes as defined
-in section \todo{ref branded objects section} their assets will lose value and
-this loss must be compensated by the ``bloggers".
-
-% TODO: Reference this:
-% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
-\subsection{Branded mathematical objects}
-We believe there has been a missed opportunity in the field of mathematics to
-increase brand awareness.
-Therefore, we propose branding mathematical objects by associating every single
-set with an individual brand.
-Brands can purchase large collections of sets at a discount.
-While most sets are cheap, some more famous sets will sell for more to reflect
-the higher market value, similar to domain names.
-Thus, ACM will create an ICANN equivalent for these sets.
-
-Authors referencing any given set must reference the brand of the set any time
-the set is referenced, regardless of the format the set is presented  in.
-Additionally, royalties must be paid to the owner of the set.
-
-We are excited to announce that our first partner in this endeavor will be
-Chili's Grill \& Bar,\footnote{Pronounced: \texts{Kill me's} The chill of severity and emptiness.} who has purchased the rights to the set of natural
-numbers.
-From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
-Natural Numbers \(\mathbb{N}\)\copyright.
-
-\subsection{ACM Classifieds}
-For additional funding we allow individuals to take out classified ads in the
-following sections.
-To keep costs low, the ACM does not vet any classified postings.
-
-\paragraph{Dropped Packets}
-Dropped Packets serves as the traditional missed connections section of the
-classifieds. While this could be used to contact that cutie from the latest
-conference, we believe that it could also be used to publicly shame those who miss meetings. A mock-up is presented in \todo{figure ref}
-
-Sample: Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.
-Sample: ``Damn it Deborah, you were supposed to bring bagels to the DARPA
-Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
-(DTA\censor{b}HBI\censor{bb}) meeting!"
-Sample: I was hiding in your closet at 54 Bishop Allen Dr.
-# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
-
-\paragraph{Job Queue}
-The Job Queue section contains odd jobs for trained Computer Scientists looking
-for instant internet income.
-Those who pay extra will get a free AirDancer\footnote{Placed at the discretion
-of the ACM in the ACM AirDancer Oasis in the Black Rock Desert in Nevada in
-solidarity with the aliens illegally detained in Area 51. The AirDancers may
-be used by the alien's to communicate with their home world about the status of the part needed to keep the AirDance of the cosmos going.}!
-We will be posting the first jobs ourselves such as,
-Snapchat is known for taking out ads in classifieds \todo{cite from LA times}.
-
-\paragraph{Overclock}
-Overclock is a section for performance enhancing drugs tailored for computer
-scientists.
-This section is mostly targeted to the Hacker News crowd who exclaims the
-benefits of small amounts of LSD for enhancing productivity at work
-\todo{cite}.
-Although we can't promote the use of illegal drugs our editor is so strung out
-on ``road cheese" that she won't notice.
-% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d
-
-\subsection{Check Scams}
+\section{Instant Internet Income}
 
@@
 In return, authors simply have to write a small check to cover transaction fees before the large check clears.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
-\caption{Have you seen this boy?}
-\end{figure}

### 2017-02-17 aesthetics.tex
oops, now i really added the aesthetics section

We should have a page that uses pretentious Clement Greenberg-esque language to talk about "perspective" and "foreground" and "background" and "depth of field" and so forth. Most papers are pretty boring: a bird's eye view. But as Freeman Dyson notes, there are birds and frogs in research. And frogs like to get in the mud. And frogs like to croak about Budweiser.

In the foreground of this page-long section, there is a giant can of Budweiser.

### 2017-02-17 aesthetics.tex
walking is my favorite thing for cats and chicks to do

@@
 In the foreground of this page-long section, there is a giant can of Budweiser.
+
+Publish untrue hit jobs on President's foes (it's not libelous if it's in ACM)
+the puzzle section/mathematical recreations just solves computational problems for businesses -- "put ACM math recreations in the loop" to get your answer with no computational overhead and a one-month delay
+
+E.g.
+suppose you are a major defense contractor Paytheon, and you've been asked to bid on a government contract with options (whose details are classified) in table A, and for each option you have a guess of the probability (table B) that the government will actually go for that option.
+Your estimated costs are in table C.
+You know your bid will be evaluated based on the overall ensemble of prices in your bid -- a weighted sum of the options with unknown weights.
+Can assign prices in such a way that you jack up the price on the things you expect the government to buy and lower the price on the things you expect the government not to buy -- with the constraint that you wish to avoid dramatic price swings that can sway the government's decision -- in such a way as to maximize expected profits?
+Can you also concoct some phony scholarship to rationalize your illegal prices, with a deck of briefing slides and a ten-page white paper?

### 2017-02-17 aesthetics.tex
what if life is just some hard equation &c &c

@@
 And frogs like to croak about Budweiser.
+And frogs are in the background.
 
@@
 Can you also concoct some phony scholarship to rationalize your illegal prices, with a deck of briefing slides and a ten-page white paper?
+
+guide to april fools day pranks that won't embarrass your teen
+old faithful superior accuracy as computer clock
+old glory which thought was old faithful but retain for it superior
+
+Academics can get around laws through fair use
+good: HEY KIDS learn how JOE CAMEL targeted kids and got them to see how COOL smoking can be
+bad (challenges authority): number theorists wrote a paper on the number-theoretic properties of "the nuclear code" numbers

### 2017-02-18 aesthetics.tex
there is a house in new orleans not the one you heard about i'm talking bout another house

@@
 bad (challenges authority): number theorists wrote a paper on the number-theoretic properties of "the nuclear code" numbers
+
+ACM pep rallies: a single academic article will be fired from a cannon but invariably so many people fight over it it just shreds to pieces
+
+ACM vending machines, human-staffed, particularly cruel topple people who stick hand in (or maybe joke about papers being can-shaped so if you try to steal one, you get stuck in the vending machine unless you decide to let go of the can.
+The Virginia state legislature has approved a measure that would allow tobacco companies to generously contribute to the ACM and the advancement of science (withheld from the wages of 14-year-old tobacco pickers), by furnishing vending machines that sell cigarette packs with snippets of technical papers on them, over the space on the pack where the Surgeon's General Warning used to go.
+Each vending machine would be affiliated with a particular ACM journal.

### 2017-02-28 digital-library.tex
Outsourced captchas

--- 2017-02-09 digital-library.tex
@@
 
-\subsection{Outsourced Captias}
-\todo{Force free-tier users to solve a captia, but the captia is actually from
-  another site and we collect money from spammers to solve these captias ala
-mechanical turk}
+\subsection{Outsourced Captchas}
+When a user requests a paper download, they will be required to submit a
+captcha.
+While many websites use captcha to prevent automated abuse, we see an
+opportunity to profit.
+We provide an API to botnets with which they may submit captchas to be
+displayed to users attempting to download files.
+Their responses to these captchas are sent back to the botnet thus allowing the
+botnet to proceed with whatever attack the captcha was preventing.
+We believe we can sell this human captcha solving service for a few cents per
+captcha.
+
+Additionally, users will not question the presence of captchas on the digital
+library as they have already been conditioned to fill captchas for all sorts of
+free services.
+As such, we do not believe that our user base will know that the ACM is
+slinging captcha solutions on the side.
 

### 2017-02-28 paper-sponsorships.tex
Outsourced captchas

--- 2017-02-09 paper-sponsorships.tex
@@
 \section{Paper Sponsorships}
+Reach the largest holistic-minded audience in the entire northeastern United
+States with an ad in the next ACM edition.
+Our public mostly devoid of energy vampires and is therefore suitable for
+empath advertisers.
+Where IEEE uses Western proof verification techniques, our broad minded
+audience validates mathematical claims in an intuitive holistic manner and will
+bring that same spirit into evaluating the claims of your advertisements.
+Our readers will engage with your brand through meditation and other
+surprises.
 

### 2017-02-28 paper-sponsorships.tex
Banner ads

@@
 \section{Paper Sponsorships}
+In addition to ads on our Digital Library, we will also be adding
+advertisements to the papers themselves.
+These advertisements will come in many forms, including standard banner
+advertisements as well as the increasingly popular native advertisement.
+
+\subsection{Call for Advertisements}
 Reach the largest holistic-minded audience in the entire northeastern United
@@
 \subsection{Banner ads}
-\todo{Autoplayed music ads.  Attempts to hijack other devices in household to
-display ACM related ads.}
+Web surfers today have become accustom to seeing banner ads on their favorite
+websites.
+Therefore, we will be incorporating these advertisements into all of our
+papers.
+Advertisements can be easily inserted into existing \LaTeX\ papers through the
+use of the \texttt{\textbackslash figure} and \texttt{\textbackslash figure*}
+constructs.
+Of course, advertisements using the two column \texttt{\textbackslash figure*}
+width will be considerably more expensive than their one column brethren.
+A standard 1 column ad can be seen in \autoref{fig:law} while a double-wide can
+be found in \autoref{fig:usa}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/law-kid-ad.png}
+\caption{Get your settlement today! \todo{attribution}}
+\label{fig:law}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\textwidth]{figures/usa-ad.png}
+\caption{We have near absolute power over you! \todo{attribution}}
+\label{fig:usa}
+\end{figure*}
+
+For an additional fee we will also allow advertisers to embed autoplaying audio
+into their paper ads.
+While we aren't currently sure whether or not the PDF specification allows
+this, we believe that there are sufficiently many ACM loving PhDs at Adobe to
+get this change  pushed into the spec.
 

### 2017-02-28 openadcess.tex
Seperated out future work
1/29 edition
Abstract

@@
-\documentclass{article}
+\documentclass[sigtbd]{sigtbd17-style}
 
+\usepackage{amsfonts}
+\usepackage{censor}
 \usepackage{color}
+\usepackage{graphicx}
+\usepackage{hyperref}
 \usepackage{xspace}
@@
 \begin{document}
+
+\title{\todo{Something} presents OpenAdcess}
+\maketitle
+
+\begin{abstract}
+  In this paper we examine an alternate funding model for open access papers.
+  Through modest modifications to the ACM Digital Library and the addition of
+  paper sponsorships we can make the entire corpus of ACM works free to the
+  public.
+  We also peer into a chilling future that only we can prevent.
+  Will we stop the ACM from encroaching on our everyday freedoms?
+  Continue existing and participating in reality to find out!
+\end{abstract}
+
 \section{Introduction}
@@
 
-\section{Paper Sponsorships}
+\input{paper-sponsorships}
 
-\section{Future Work}
-\todo{Crazy dystopian future stuff here}
+\input{future-work}
 

### 2017-02-28 future-work.tex
Linden dollars are the currency of the future

@@
 To those who dislike the ads they see, ACM will offer a premium version for
-\todo{some amount of money} per year.
+2000 Linden dollars per year \footnote{In the future Linden dollars are the
+one true world currency.
+The value of 2000 L\$ in today's United States Dollar is currently unknown.}.
 Unfortunately, due to high credit card processing fees we must still show ads

### 2017-02-28 introduction.tex
Took a stab at the intro

\section{Introduction}
Open access is a movement to make papers and other research contributions free
accessible to the general public \todo{cite}.
The ACM has been working for some time to achieve the open access dream but
have found the dream to be prohibitively expensive \todo{cite}.
To fund this venture, we have chosen to adopt the techniques employed by
various other websites and publications that manage to distribute content for
free.

Section~\ref{sec:related} details techniques used by other services to achieve free
downloads and paper distribution.
Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
bring it up to current standards for download portals.
Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that papers
themselves are profitable.
Section~\ref{sec:future} describes a future that directly results from the
publication of this paper.
We provide this look into the future so that we may attempt to contain the
beast that is the ACM while still providing free papers to all.

### 2017-02-28 digital-library.tex
Took a stab at the intro
Related work

@@
 \section{Digital Library}
+\label{sec:lib}
 Shady websites have long managed to monetize content downloads.
@@
 \subsection{Fake Download Buttons}
+\label{sec:fake}
 
@@
 \subsection{Rate Limited Free Downloads}
+\label{sec:limit}
 Free download sites figured out long ago that you can make people pay for an

### 2017-02-28 paper-sponsorships.tex
Took a stab at the intro
Related work

@@
 \section{Paper Sponsorships}
+\label{sec:sponsors}
 In addition to ads on our Digital Library, we will also be adding
@@
 \subsection{Branded mathematical objects}
+\label{sec:brands}
 We believe there has been a missed opportunity in the field of mathematics to

### 2017-02-28 related-work.tex
Related work

\section{Related Work}
\label{sec:related}

Download.com \cite{download-com} provides free downloads of popular programs to
the public.
We borrow their idea of using misleading advertisements to trick users into
downloading programs they may not want in \autoref{sec:fake}.

Rapidshare \cite{rapidshare} was a website that provided rate limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists it seems that this technique
alone is insufficient to cover the costs of running a download service.
However, we still employ the technique as explained in \autoref{sec:limit} as a
supplemental revenue stream.

\todo{Harvest paper} and many other free rags employ heavy use of in paper ads,
native ads, and classifieds.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.

Edsger W. Dijkstra has previously proposed the revolutionary idea of
capitalizing mathematics \cite{cap-math}.
We expand on this idea with our branded mathematical objects in
\autoref{sec:brands}.

### 2017-03-01 future-work.tex
Took a stab at the intro
Hecka citations

@@
 \section{Future Work}
+\label{sec:future}
 This future work appears in SIGTBD \todo{citation to future
@@
 \subsection{Future Work}
-A consequence of the invention of time travel \todo{Cite paper} and the vanity
+A consequence of the invention of time travel \cite{time-travel} and the vanity
 of engineers (not scientests) \todo{Cite ubiquity article} is that people
@@
 Our report of our screwing missadventuresduring our fieldtrip into the past can
-be seen here: \todo{Citation to future article: 1984 esque ACM IS EVERYWHERE,
-ACM IS UBIQUITY, WE LOVE ACM}
-ubiquity paper}
+be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.
 

### 2017-03-01 introduction.tex
Hecka citations

@@
 Open access is a movement to make papers and other research contributions free
-accessible to the general public \todo{cite}.
+accessible to the general public \cite{oa}.
 The ACM has been working for some time to achieve the open access dream but
-have found the dream to be prohibitively expensive \todo{cite}.
-To fund this venture, we have chosen to adopt the techniques employed by
-various other websites and publications that manage to distribute content for
-free.
+have found this dream to be prohibitively expensive.
+As such, we have required authors to opt-in to open access by paying the cost
+themselves \todo{cite (and archive current authors.acm.org page)}.
+However, we have found a way to provide open access papers at no cost to the
+authors by adopting the techniques employed by various other websites and
+publications that manage to distribute content for free.
 

### 2017-03-01 paper-sponsorships.tex
Hecka citations

@@
 \includegraphics[width=0.45\textwidth]{figures/law-kid-ad.png}
-\caption{Get your settlement today! \todo{attribution}}
+\caption{Get your settlement today \cite{med-scale}!}
 \label{fig:law}
@@
 \includegraphics[width=0.95\textwidth]{figures/usa-ad.png}
-\caption{We have near absolute power over you! \todo{attribution}}
+\caption{We have near absolute power over you \cite{eagle, kanye, microwave}!}
 \label{fig:usa}
@@
 We require that the company logo is a stylized version of the letter being
-replaced to avoid a Wingdings situation \todo{Cite NYC controversy}.
+replaced to avoid a Wingdings situation \cite{wingdings}.
 
@@
 benefits of small amounts of LSD for enhancing productivity at work
-\todo{cite}.
+\cite{microdose, lsd-song}.
 Although we can't promote the use of illegal drugs our editor is so strung out

### 2017-03-01 related-work.tex
Hecka citations
More wisdom

@@
 
-\todo{Harvest paper} and many other free rags employ heavy use of in paper ads,
+Wisdom \cite{wisdom} and many other free rags employ heavy use of in paper ads,
 native ads, and classifieds.
@@
 \autoref{sec:sponsors}.
+Additionally, Wisdom claims most holism but we have the narrow computational
+tools to prove that we are more holistic.
 

### 2017-03-01 future-work.tex
Mo citations mo problems

@@
 \label{sec:future}
-This future work appears in SIGTBD \todo{citation to future
-paper edition}.
-
-\todo{All crazy future ideas go here.
-Verification snacks, etc.}
+This future work appears in a compilation of great speaches from the ACM
+\cite{acm-state}.
 
@@
 A consequence of the invention of time travel \cite{time-travel} and the vanity
-of engineers (not scientests) \todo{Cite ubiquity article} is that people
-keep going further back in time to give themselves credit for the invention of
-the time machine.
+of engineers (not scientests) \cite{sci-shirt} is that people keep going
+further back in time to give themselves credit for the invention of the time
+machine.
 However, we propose to go back in time for a different reason.

### 2017-03-01 paper-sponsorships.tex
Mo citations mo problems

@@
 be used by the alien's to communicate with their home world}!
-We will be posting the first jobs ourselves such as,
-Snapchat is known for taking out ads in classifieds \todo{cite from LA times}.
+We will be posting the first jobs ourselves.
 
@@
 scientists.
-This section is mostly targeted to the Hacker News crowd who exclaims the
-benefits of small amounts of LSD for enhancing productivity at work
+This section is mostly targeted to the Hacker News \cite{hn} crowd who exclaims
+the benefits of small amounts of LSD for enhancing productivity at work
 \cite{microdose, lsd-song}.

### 2017-03-01 digital-library.tex
Misc fill ins

@@
 
-The free tier will only allow downloads at \todo{rate} and no more than one
-paper download per day.
-Additionally, the user will be required to watch an upgrade screen
-\todo{explain this} count down for 10 minutes before the download button is
+The free tier will only allow downloads at slow speeds and no more than one
+paper per day.
+Additionally, the user will be required to stare at a screen compelling them to
+upgrade while a counter decrements for 10 minutes before the download button is
 clickable.
 If the website loses focus, the counter will be restarted.
-The \premium tier will cost \todo{rate} but will allow unlimited downloads and
-will not be rate limited.
+The \premium tier will allow unlimited downloads and will not be rate limited.
 

### 2017-03-01 paper-sponsorships.tex
Misc fill ins

@@
 \subsection{Native Ads}
-\todo{Define native advertising}
+Native advertisements are advertisements meant to be disguised among the normal
+content of a publication.
+They are written in the same style as the publication and appear alongside
+unsponsored content in an attempt to make the reader believe that they are
+reading the original publication and not an advertisement \cite{native}.
 
@@
 will result in a strong reject of the paper.
-The ad section must be at least one page long, but there is upper bound on
+The ad section must be at least one page long, but there is no upper bound on
 native ad length.
@@
 
-\subsection{Investor Author Dispute Settlement}
-We have founded an Investor Author Dispute Settlement (IADS) court to protect
-businesses from results that may damage their reputation or profits.
-If a research project is found to be damaging, the authors must either retract
-the paper or pay a settlement equal to the estimated losses suffered by the
-company.
-For example, if some agitator finds that the complexity class PLS is in PPP
-relative to some oracle will dash the hopes of the typical \todo{brand}
-consumer.
-Moreover, since \todo{brand} owns both of these complexity classes as defined
-in section \todo{ref branded objects section} their assets will lose value and
-this loss must be compensated by the ``bloggers".
-
-% TODO: Reference this:
-% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
 \subsection{Branded mathematical objects}
@@
 
+\subsection{Investor Author Dispute Settlement}
+We have founded an Investor Author Dispute Settlement (IADS) court to protect
+businesses from results that may damage their reputation or profits.
+If a research project is found to be damaging, the authors must either retract
+the paper or pay a settlement equal to the estimated losses suffered by the
+company.
+For example, if some agitator finds that the complexity class PLS is in PPP
+relative to some oracle will dash the hopes of the typical Sparrow Soap
+consumer they may use the IADS court to mitigate their losses from this
+finding.
+Moreover, since Sparrow Soap owns both of these complexity classes as defined
+in section \autoref{sec:brands} their assets will lose value and
+this loss must be compensated by the ``bloggers."
+
 \subsection{ACM Classifieds}
@@
 classifieds.
-While this could be used to contact that cutie \todo{sp?} from the latest
-conference, we believe that it could also be used to publicly shame those who
-miss meetings.
+While this could be used to contact that cutie from the latest conference, we
+believe that it could also be used to publicly shame those who miss meetings.
 For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA

### 2017-03-01 conclusion.tex
Conclusion and future work fill ins

\section{Conclusion}
By bringing ACM up to date with the latest advertising techniques described in
this paper we believe that we can finally provide our papers to the masses for
free and at no cost to the authors.
Unfortunately, our trip to the future indicates that this idea works all too
well.
We release this knowledge onto the world knowing that the next generation must
pay for our free papers today with their work in the ACM dungeons and surrender
of their corporation.
We hope that future generations will somehow stop the beast that is the ACM
before it grows too powerful, but our own desire for fame outweighs our desire
to save our children from this madness.

### 2017-03-01 future-work.tex
Conclusion and future work fill ins

@@
 \subsection{Subvert Academic Thought}
-\todo{Pivot academic thought away from mathematical and computational problems.
-Wasted  brainpower when they could be thinking about products and brands.}
+Our native advertising proposal contained within the revolutionary Open Adcess
+\cite{this} paper was much more effective than we ever could have imagined at
+the time.
+Rather than simply increasing brand awareness, we were able to transform
+academic thinking away from mathematical and computational problems and
+instead onto products and brands.
+Computer scientists today have solved the worlds biggest problems in branding
+and marketing while believing they were wasting all that brainpower on math.
 
 \subsection{ACM Seizes Means of Production}
-\todo{By putting crushed crystals in CEO's coffee, the ACM will influence CEOs
-  to liquidate their companies and give them to the ACM.
-  The mills were originally for crushing crystals but after the revolution they
-were re purposed to generate electricity
-ESPN executives are Mormon though and impervious to crystal healing and coffee. So we had to compromise: the entire National Park System became an ESPN Zone.
-}
+The ACM has successfully seized the means of production.
+The mills that are now used to power our servers were previously used to grind
+healing crystals into a fine powder.
+This powder was slipped into the coffee of unsuspecting CEOs where it worked to
+slowly make them more acceptable to the messages of the ACM.
+After years of crystal ingestion, the CEOs of the world's largest companies
+ceded control of their companies to the ACM.
+We are happy to announce that there currently exist no companies other than the
+ACM.
 
@@
 
-\todo{Servers powered by manual labor (guy in basement pushing bar around).  If
-you want an ad free version you can visit your local ACM work dungeon to
-manually turn a generator.)}
-
-\todo{Set system clock to run 10 to the 8 times slower than real time for
-reporting performance numbers as recommended by
-https://queue.acm.org/detail.cfm?id=3036398}
+%Set system clock to run 10 to the 8 times slower than real time for
+%reporting performance numbers as recommended by
+%https://queue.acm.org/detail.cfm?id=3036398

### 2017-03-01 conclusion.tex
Draft pass

@@
 We release this knowledge onto the world knowing that the next generation must
-pay for our free papers today with their work in the ACM dungeons and surrender
-of their corporation.
+pay for our free papers with their work in the ACM dungeons and surrender of
+their corporations.
 We hope that future generations will somehow stop the beast that is the ACM

### 2017-03-01 digital-library.tex
Draft pass

@@
 \label{sec:lib}
-Shady websites have long managed to monetize content downloads.
-To provide free access to papers, we can follow their model by making the
-following changes.
+Shady websites have long managed to monetize free content downloads.
+Below we detail the ways in which we can follow their example to provide free
+access to papers.
 
@@
 Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good.
-But you still shouldn?t eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically.
+But you still shouldn't eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically.
 It should be impossible for consumers to access independent, third-party statistics about menu items.
@@
 \subsection{ACM Digital Library Toolbar}
-Like Java, every ACM paper will come as an executable.
+Every ACM paper will be distributed as an executable.
 Running this executable will ``install" the paper to the users desktop.
-The only purpose of the install is to push the ACM Digital Library toolbar.
+The only purpose of the install is to push the ACM Digital Library toolbar on
+the user.
 While the toolbar itself is optional, its installation is opt-out.
-The ACM DL toolbar will be installed for all of the users web browsers where it
+The ACM DL toolbar will be installed for the user's web browsers where it
 will follow them from site to site collecting information about their browsing
@@
 attack to seize control of the network for our own financial gain.
+
+In order to comply with New Jersey's backwards laws about involuntary Bitcoin
+mining \cite{tidbit}, all New Jersey residents will be preemptively banned from
+the ACM Digital Library.

### 2017-03-01 future-work.tex
Draft pass

@@
 \paragraph{Introduction} An introduction is an explanatory section of a document that introduces the topic discussed in the document and presents a thesis statement.
-\paragraph{Antithesis} Think about it, man. There is not introduction. We just see bad writing, cast as we are into this broken world.
-\paragraph{Sublation} The introduction, some may argue
-
+\paragraph{Antithesis} Think about it, man. There is no introduction. We just see bad writing, cast as we are into this broken world.
+\iffalse
+% Temporarily removed because I have no idea what this is
+\paragraph{Sublation}
 We think introductions leave those catching up with a field disoriented.
@@
 As you may recall from \todo{sublation}, the engineers have ended the industrial dictatorship of the captains of finance as a matter of convenience
+\fi
 
@@
 one true world currency.
-The value of 2000 L\$ in today's United States Dollar is currently unknown.}.
+The value of 2000 L\$ in today's United States Dollar is not known.}.
 Unfortunately, due to high credit card processing fees we must still show ads
@@
 with more ``refined" tastes.
-We hope to solve this issue in the future with the creation of Bank of ACM.
+We hope to solve this issue in the future with the creation of The Bank of ACM.
 
@@
 necessary electricity required to power our servers.
-However, all of this electricity is used to power electric lumbar support for
-OSHA employees in exchange for their continued appreciation of the safe
-practises within our work dungeons.
+However, all of this electricity is currently used to power electric lumbar
+support for OSHA employees in exchange for their continued appreciation of the
+safe practises within our work dungeons.
 Two months of full time service provides access to five ad-free papers.
@@
   \includegraphics[width=0.45\textwidth]{figures/mill.png}
-  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how our graduate students show great vigor and -- auscultate away! -- don't sound consumptive.}
+  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how
+  our graduate students show great vigor!}
   \label{fig:mill}
@@
   \includegraphics[width=0.45\textwidth]{figures/horse-mill.jpg}
-  \caption{12th year grad student sentenced to extra
-  month in work dungeon for insufficient commitment to the mission of advancing
+  \caption{Lazy 12th year grad student sentenced to an extra
+  month in the work dungeon for insufficient commitment to the mission of advancing
 computing as a science and profession.
 Not only is he a lifetime ACM member, but he's a lifehacker!  Shown here in his
-ergonomic harness and standing desk.
-OSHA would be proud.}
+ergonomic harness and standing desk.}
   \label{fig:horse-mill}
@@
 academic thinking away from mathematical and computational problems and
-instead onto products and brands.
+onto products and brands.
 Computer scientists today have solved the worlds biggest problems in branding
@@
 This powder was slipped into the coffee of unsuspecting CEOs where it worked to
-slowly make them more acceptable to the messages of the ACM.
+slowly make them more susceptible to the messages of the ACM.
 After years of crystal ingestion, the CEOs of the world's largest companies
@@
 mill and share healing crystals.
-Our report of our screwing missadventuresduring our fieldtrip into the past can
-be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.
+Our report of our screwing missadventures during our field trip into the past
+can be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.
 

### 2017-03-01 paper-sponsorships.tex
Draft pass

@@
 These advertisements will come in many forms, including standard banner
-advertisements as well as the increasingly popular native advertisement.
+advertisements as well as increasingly popular native advertisements.
 
@@
 States with an ad in the next ACM edition.
-Our public mostly devoid of energy vampires and is therefore suitable for
-empath advertisers.
+Our readership is mostly devoid of energy vampires and is therefore suitable
+for empath advertisers.
 Where IEEE uses Western proof verification techniques, our broad minded
@@
 Of course, advertisements using the two column \texttt{\textbackslash figure*}
-width will be considerably more expensive than their one column brethren.
-A standard 1 column ad can be seen in \autoref{fig:law} while a double-wide can
-be found in \autoref{fig:usa}.
+construct will be considerably more expensive than their one column brethren.
+A standard single column ad can be seen in \autoref{fig:law} while a
+double-wide can be found in \autoref{fig:usa}.
 
@@
 \subsection{Ad Enhanced Fonts}
-Computer Modern is a staple of modern papers, but we believe that this font can
+Computer Modern is a staple of today's papers, but we believe that this font can
 be monetized.
-By replacing the characters in the default latex with logos of companies we can
-convey the same information in an ad enhanced way.
+By replacing the characters in the default \LaTeX\ font with corporate logos
+we can convey the same information in an ad enhanced way.
 
-During each Call for Papers we will also put out a simultaneous Call for
-Logos during which companies bid on which letter they want.
-We require that the company logo is a stylized version of the letter being
-replaced to avoid a Wingdings situation \cite{wingdings}.
+During each call for papers we will also put out a simultaneous call for
+logos where companies can bid on desirable letters.
+To avoid a Wingdings situation \cite{wingdings}, we require that the company
+logo is a stylized version of the letter being replaced.
 
@@
 that was assigned to the research project.
-As these ads are to be native, an advertisement that is recognizable as an ad
-will result in a strong reject of the paper.
+As these ads must be indistinguishable from the rest of the paper, an
+advertisement that is recognizable as an ad will result in the rejection of the
+paper.
 The ad section must be at least one page long, but there is no upper bound on
@@
 Brands can purchase large collections of sets at a discount.
-While most sets are cheap, some more famous sets will sell for more to reflect
-the higher market value, similar to domain names.
-Thus, ACM will create an ICANN equivalent for these sets.
+While most sets are cheap, some more famous sets will be priced higher to
+reflect their higher market value, similar to domain names.
 
@@
 From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
-Natural Numbers \(\mathbb{N}\)\copyright.
+Natural Numbers \(\mathbb{N}\).
 
@@
 For example, if some agitator finds that the complexity class PLS is in PPP
-relative to some oracle will dash the hopes of the typical Sparrow Soap
-consumer they may use the IADS court to mitigate their losses from this
-finding.
+relative to some oracle, they will dash the hopes of the typical Sparrow Soap
+consumer.
+Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
+this finding.
 Moreover, since Sparrow Soap owns both of these complexity classes as defined
@@
 solidarity with the aliens illegally detained in Area 51.  The AirDancers may
-be used by the alien's to communicate with their home world}!
+be used by the alien's to communicate with their home world.}!
 We will be posting the first jobs ourselves.
@@
 scientists.
-This section is mostly targeted to the Hacker News \cite{hn} crowd who exclaims
+This section is mostly targeted at the Hacker News \cite{hn} crowd who exclaims
 the benefits of small amounts of LSD for enhancing productivity at work

### 2017-03-01 digital-library.tex
Spelling

@@
 While the toolbar itself is optional, its installation is opt-out.
-The ACM DL toolbar will be installed for the user's web browsers where it
+The ACM Digital Library toolbar will be installed for the user's web browsers where it
 will follow them from site to site collecting information about their browsing

### 2017-03-01 future-work.tex
Spelling

@@
 \label{sec:future}
-This future work appears in a compilation of great speaches from the ACM
+This future work appears in a compilation of great speeches from the ACM
 \cite{acm-state}.
@@
 support for OSHA employees in exchange for their continued appreciation of the
-safe practises within our work dungeons.
+safe practices within our work dungeons.
 Two months of full time service provides access to five ad-free papers.
@@
 A consequence of the invention of time travel \cite{time-travel} and the vanity
-of engineers (not scientests) \cite{sci-shirt} is that people keep going
+of engineers (not scientists) \cite{sci-shirt} is that people keep going
 further back in time to give themselves credit for the invention of the time
@@
 mill and share healing crystals.
-Our report of our screwing missadventures during our field trip into the past
+Our report of our screwing misadventures during our field trip into the past
 can be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.

### 2017-03-31 introduction.tex
Mo citations mo problems
A couple of small changes

@@
 \section{Introduction}
-Open access is a movement to make papers and other research contributions free
-accessible to the general public \cite{oa}.
+Open access is a movement to make papers and other research contributions
+freely accessible to the general public \cite{oa}.
 The ACM has been working for some time to achieve the open access dream but
@@
 As such, we have required authors to opt-in to open access by paying the cost
-themselves \todo{cite (and archive current authors.acm.org page)}.
+themselves \cite{auth}.
 However, we have found a way to provide open access papers at no cost to the
-authors by adopting the techniques employed by various other websites and
+authors by adopting the techniques employed by various websites and
 publications that manage to distribute content for free.
 
-Section~\ref{sec:related} details techniques used by other services to achieve free
-downloads and paper distribution.
+Section~\ref{sec:related} details techniques used by other services to achieve
+free downloads and paper distribution.
 Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
-bring it up to current standards for download portals.
-Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that papers
-themselves are profitable.
-Section~\ref{sec:future} describes a future that directly results from the
-publication of this paper.
-We provide this look into the future so that we may attempt to contain the
-beast that is the ACM while still providing free papers to all.
+bring it up to the current standards for download portals.
+Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that
+the papers themselves are profitable.
+Section~\ref{sec:future} provides work from a future that directly results from the present work.

### 2017-03-31 related-work.tex
Draft pass
A couple of small changes

--- 2017-02-28 related-work.tex
@@
 
-Rapidshare \cite{rapidshare} was a website that provided rate limited free
+Rapidshare \cite{rapidshare} was a website that provided rate-limited free
 downloads while simultaneously selling a paid download service that was
@@
 This technique was meant to entice users to pay for the service.
-Unfortunately, as Rapidshare no longer exists it seems that this technique
-alone is insufficient to cover the costs of running a download service.
-However, we still employ the technique as explained in \autoref{sec:limit} as a
-supplemental revenue stream.
+Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service.
+Or maybe they did not take this technique far enough.
+He he he.
 
-\todo{Harvest paper} and many other free rags employ heavy use of in paper ads,
-native ads, and classifieds.
+Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
+native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
 We also adopt these techniques to embed in all of our papers in

### 2017-04-08 digital-library.tex

@@
 ``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them.
-We don't want the government treating them like dotards," the Gary Cohns said in unison.}.
+We don't want the government treating them like dotards," Gary Cohn said to the lobbyists who inform and engage him.}.
 
@@
 the ACM Digital Library.
+
+\subsection{Impact Factor-ometer}
+
+Researchers want their projects to have meaning and impact.
+Administrators like to market their department's product as meaningful and impactful.
+But how can researchers tell their work is saving the world?
+
+Simple.
+Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer.
+As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}
+
+\begin{figure}
+  \centering
+  %https://archive.org/details/414803main_0203243
+  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
+  \caption{A model-year 1985 Noisome-ter, prized by collectors for its muted design that limns adumbrations of sound.
+The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
+  \label{fig:noiseometer}
+\end{figure}
+
+These metrics empower our research partners to be certain their research is having a real-world impact.
+It is important for researchers to know that they don't risk deactivation or exile if they remain on track.

### 2017-04-08 introduction.tex

@@
 the papers themselves are profitable.
-Section~\ref{sec:future} provides work from a future that directly results from the present work.
+Section~\ref{sec:future} describes a future that directly results from the
+publication of this paper.
+We provide this look into the future so that we may attempt to contain the
+beast that is the ACM while still providing free papers to all.

### 2017-04-08 paper-sponsorships.tex

@@
 By replacing the characters in the default \LaTeX\ font with corporate logos
-we can convey the same information in an ad enhanced way.
+we can convey the same information in an ad enhanced way. The inspiring example of Claude Shannon proves it!
 
@@
 Dropped Packets serves as the traditional missed connections section of the
-classifieds.
+classifieds. While this could be used to contact that cutie from the latest
 While this could be used to contact that cutie from the latest conference, we
 believe that it could also be used to publicly shame those who miss meetings.
-For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA
+
+Sample: Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.
+
+Sample: ``Damn it Deborah, you were supposed to bring bagels to the DARPA
 Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
 (DTA\censor{b}HBI\censor{bb}) meeting!"
+Sample: I was hiding in your closet at 54 Bishop Allen Dr.
+# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
 
@@
 solidarity with the aliens illegally detained in Area 51. The AirDancers may
-be used by the alien's to communicate with their home world.}!
-We will be posting the first jobs ourselves.
+be used by the aliens to communicate with their home world about the status of the part needed to keep the AirDance of the cosmos going.}!
 

### 2017-04-08 aesthetics.tex
added some files

@@
 
-ACM pep rallies: a single academic article will be fired from a cannon but invariably so many people fight over it it just shreds to pieces
+ACM pep rallies: a single academic article will be fired from a t-shirt cannon but invariably so many people fight over it it just shreds to pieces
 
@@
 Each vending machine would be affiliated with a particular ACM journal.
+
+jewel heists for the ACM, decadent society gadabout for the ACM
+
+ACM rigged casino PL
+
+We can't have papers floating around everywhere. A researcher is liable to make a pass at the Truth.

### 2017-04-09 paper-sponsorships.tex
a couple small modifications to three files

--- 2017-03-01 paper-sponsorships.tex
@@
 Reach the largest holistic-minded audience in the entire northeastern United
-States with an ad in the next ACM edition.
+States with an ad in the next ACM edition.\footnote{Wisdom disputes this claim, but we have the narrow computational tools to prove our publication and community have way more holism.}
 Our readership is mostly devoid of energy vampires and is therefore suitable

### 2017-04-09 related-work.tex
a couple small modifications to three files

@@
 This technique was meant to entice users to pay for the service.
-Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service.
-Or maybe they did not take this technique far enough.
-He he he.
+Unfortunately, as Rapidshare no longer exists it seems that this technique, used alone,
+alone is insufficient to cover the costs of running a download service. Or maybe they did not take this idea far enough. He he he.
 
-Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
-native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
+Wisdom \cite{wisdom} and many other free rags make such heavy use of traditional print ads,
+native ads, and classifieds that paper copies may profitably be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
 We also adopt these techniques to embed in all of our papers in
 \autoref{sec:sponsors}.
+Additionally, Wisdom claims most holism but we have the narrow computational
+tools to prove that we are more holistic.
 

### 2017-04-10 openadcess.tex
Took a stab at the intro
Related work
Conclusion and future work fill ins

@@
 
-\title{\todo{Something} presents OpenAdcess}
+\title{BurgerTown Presents: Open Adcess}
 \maketitle
@@
   Through modest modifications to the ACM Digital Library and the addition of
-  paper sponsorships we can make the entire corpus of ACM works free to the
-  public.
-  We also peer into a chilling future that only we can prevent.
-  Will we stop the ACM from encroaching on our everyday freedoms?
+  paper sponsorships, we can make the entire corpus of ACM works free to the
+  public. What does the future have in store for the open-adcess movement?
   Continue existing and participating in reality to find out!
@@
 
-\section{Introduction}
+\input{introduction}
 
-\section{Related Work}
+\input{related-work}
 
@@
 
+\input{conclusion}
+
+\bibliography{references}{}
+\bibliographystyle{plain}
+
 \end{document}

### 2017-04-14 paper-sponsorships.tex
conflicts of interest

@@
 
-\subsection{Investor Author Dispute Settlement}
-We have founded an Investor Author Dispute Settlement (IADS) court to protect
+\subsection{Investor Science Dispute Settlement}
+We have founded an Investor Science Dispute Settlement (ISDS) court to protect
 businesses from results that may damage their reputation or profits.
@@
 relative to some oracle, they will dash the hopes of the typical Sparrow Soap
-consumer.
+consumer, leading to hygiene neglect.
 Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
@@
 in section \autoref{sec:brands} their assets will lose value and
-this loss must be compensated by the ``bloggers."
+this loss must be compensated by the offending authors.
+Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption.
+These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system.
+Much as the visionary rulings of Anthony Kennedy and others have opened up our politics to make it more responsive to democratic speech, ISDS will make science more responsive to the needs of democratic actors, like 501(c)(4) ``social welfare" nonprofits.
+Welfare!
+It will democratize our understanding of reality, taking science out of the smooth, mildly scented ivory tower and cramming it into the ad-plastered public square.
+Science is agoraphobic but its future is in the agora of the brainscape---the marketplace of ideas---so (to coin a term) ISDS is the deagoraphobification of science.
+Science cannot ignore society.
+Science must come to where the flavor is.
+
+What of the science that does get published?
+The agents who do get economically controversial results published---the humble, modest, yeoman-scientist free agents---are likely to be powerful entities in a society with concentrated private economic power, some argue.
+How is that democratic?
+Well, Madison got it right.
+It's not only democratic, it's the purest form of democracy: the ``mischief of the factions." Simply put, ISDS provides a powerful mechanism of checks and balances.
+If Hot Packets wants to get their signature snack food placed on the government's food pyramid, it would need peer-reviewed science attesting to its beneficial health effects (such as an appearance on the Doctor Conflict-of-Interest show, where the titular doctor attests to its miracle superfood status, or a research paper).
+To appear in print, it would have to pay off claims from competing superfoods such as Berry Loops or Jazz Flakes.
+The system works!
+But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and lack of monopsony would have little trouble passing ISDS.
 

### 2017-04-14 paper-sponsorships.tex
economic terrorists

@@
 this loss must be compensated by the offending authors.
+
 Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption.
@@
 The system works!
-But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and lack of monopsony would have little trouble passing ISDS.
+But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and questioning Robinsonian labor market monopsony would have little trouble passing ISDS.
+Approved ideas get approved quickly, and the system works!
+
+ISDS also applies to scientists in their personal lives.
+If a scientist, for instance, posts to social media video of an alleged bad encounter with an internet service provider's customer service representative or video of hose water burning---and ISDS tribunal statisticians (employees of the ISDS corporate community, on rotation) determine that, as a result of these actions, shareholders lost value---then the economic terrorists promulgating this ticker-tanking tripe will have to compensate all shareholders for the drop in share price, as well as the social media platform monopoly's shareholders (if applicable; scientists should not be using free, distributed social networks but may use privately held proprietary platforms) for the shame they've brought to the platform even if share price was unaffected.
+This way, the integrity of the scientific process is protected---and scientists represent science with honor---in all spheres, not just peer-reviewed journals.
 

### 2017-04-19 paper-sponsorships.tex
updated notion of scientific truth

@@
 
-Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption.
+Several ``bloggers" and fuddy-duddies fixated on a staid notion of ``truth" (lacking the agility and dynamism that characterize a proactive, change-driven science) have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption.
 These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system.

### 2017-04-23 ideas.tex
current

* one of the links referenced is a terrifying URL that ends in .exe

* Featurette: Does Commercialism Chill Scientific Inquiry (sponsored by Chill's restaurant): Take a look at science -- people valorize metrics, hack p-values, hype results for media coverage and access to scarce research funds, try to boot the ego. Paul Erd\"os may have been right about math but he's wrong about science. Science is a machine for converting sacred principles (openness) and good-to-the-last-drop Maxwell House coffee ("We gave you a Haggadah. It's the least you could do.") into profane, Taylorizable metrics (openness scores). Science is a rat race already. The introduction of incentives for commercial relevance need not constrain the liberty of researchers. Is the pursuit of science that is flattering to the scientist any different than the pursuit of science flattering to the all-new 2017 Jep Liberty? Discuss the latest research about the miracle superfood bacon-wrapped rib nachos at your neighborhood Chill's today!

* Don't think that the easy-to-grasp numbers are necessarily more widely grasped. The ACM children's program, \emph{Shareware Street}, in a disgusting commercial display, infamously allows the numbers with the deepest pockets to sponsor its programming. Consequently, some brands may choose to purchase numbers more abstruse (i.e., admitting no obvious simple English formulation) that they may have money the more with which to bribe \emph{Shareware Street} producers.

* Keep in mind, while sponsors purchase naming rights based on a \emph{description} of a number or set, they are in fact purchasing the number itself. If a speculator purchases, based on a description, a number that turns out not to exist, the speculator is left with nothing, whereas the purchaser of the paradox---the giving a name to a non-existent thing---involving the description, would remain a sponsor of the paradox if it is indeed a valid paradox. If someone purchases, based on description, a number that is already sponsored by another entity, she owes that entity 50 push-ups.

### 2017-04-23 paper-sponsorships.tex
Compiles

@@
 We are excited to announce that our first partner in this endeavor will be
-Chili's Grill \& Bar,\footnote{Pronounced: \texts{Kill me's} The chill of severity and emptiness.} who has purchased the rights to the set of natural
+Chili's Grill \& Bar,\footnote{Pronounced: ``Kill me's'' The chill of severity and emptiness.} who has purchased the rights to the set of natural
 numbers.
@@
 Sample: I was hiding in your closet at 54 Bishop Allen Dr.
-# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
+\# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
 
@@
 Recent accounting innovations surveyed in two review articles and one major motion picture ["Consumer Information: Fake Checks"
-https://www.consumer.ftc.gov/articles/0159-fake-checks; "Counterfeit Check Scams: CONSUMER ALERT" http://www.michigan.gov/ag/0,4534,7-164-17337_20942-176356--,00.html; \textit{Bridget Jones's Check Scam} distributed by Universal Pictures] enable the ACM to write large checks to authors.
+https://www.consumer.ftc.gov/articles/0159-fake-checks; "Counterfeit Check
+Scams: CONSUMER ALERT" http://www.michigan.gov/ag/0,4534,7-164-17337\_20942-176356--,00.html; \textit{Bridget Jones's Check Scam} distributed by Universal Pictures] enable the ACM to write large checks to authors.
 In return, authors simply have to write a small check to cover transaction fees before the large check clears.

### 2017-04-23 paper-sponsorships.tex
typos

@@
 Dropped Packets serves as the traditional missed connections section of the
-classifieds. While this could be used to contact that cutie from the latest
+classifieds.
 While this could be used to contact that cutie from the latest conference, we
 believe that it could also be used to publicly shame those who miss meetings.
+Some examples include:
 
-Sample: Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.
+\begin{enumerate}
+  \item Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.
 
-Sample: ``Damn it Deborah, you were supposed to bring bagels to the DARPA
+  \item Damn it Deborah, you were supposed to bring bagels to the DARPA
 Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
-(DTA\censor{b}HBI\censor{bb}) meeting!"
-Sample: I was hiding in your closet at 54 Bishop Allen Dr.
+(DTA\censor{b}HBI\censor{bb}) meeting!
+
+  \item I was hiding in your closet at 54 Bishop Allen Dr.
 \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
+\end{enumerate}
 

### 2017-04-23 digital-library.tex
current
?

@@
 Below we detail the ways in which we can follow their example to provide free
-access to papers.
+access to papers and liberate the ACM reader from covetousness.
 
@@
 clickable.
-If the website loses focus, the counter will be restarted.
+If the engagement of the user---monitored via gaze tracker and wearable heart-rate monitor---falls below the zone of synergy, the counter will be restarted.
 The \premium tier will allow unlimited downloads and will not be rate limited.
@@
 Every ACM paper will be distributed as an executable.
-Running this executable will ``install" the paper to the users desktop.
+Running this executable will ``install" the paper to the user's desktop.
 The only purpose of the install is to push the ACM Digital Library toolbar on
@@
 mining \cite{tidbit}, all New Jersey residents will be preemptively banned from
-the ACM Digital Library.
+the ACM Digital Library and the greater academic community.
 

### 2017-04-23 digital-library.tex
Hella revisions

@@
 
-Fake download buttons are a staple of modern download websites.
-They really class up the web.
-Reifying, elegizing, and idealizing nature, these abstract forms with rococo garnishes direct the downloader's attention away from the url to the ad-serving service to which the button points.
-A deceptive d\'{e}tournement, the premonitory placement of these blissed-out buttons challenges browsers to consider whether they really want to download the paper -- they could, after all, not pursue their line of inquiry and instead watch it evolve vicariously -- which cuts down on the ACM's hosting costs.
+Fake download buttons are a staple of modern download websites. They really
+class up the web. Reifying, elegizing, and idealizing nature, these abstract
+forms  direct the downloader's attention away from the url
+to the ad-serving service to which the button points. A deceptive
+d\'{e}tournement, the placement of these blissed-out buttons
+challenges browsers to consider whether they really want to download the paper.
+They could, after all, choose to abandon their line of inquiry and instead
+watch their field's evolution vicariously through mainstream media, which cuts
+down on the ACM's hosting costs.
 
@@
 is redirected to see the advertiser's product while the ACM gets the revenue
-for an impression.
-Some regulators have questioned this practice.
-But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J.
-Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good.
-But you still shouldn't eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically.
-It should be impossible for consumers to access independent, third-party statistics about menu items.
-``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them.
-We don't want the government treating them like dotards," Gary Cohn said to the lobbyists who inform and engage him.}.
+for an impression. Some regulators have questioned this practice. But we
+believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of
+  the National Economic Council, stressed in an interview with \textit{The Wall
+Street Journal} compared a website without fake-download buttons to the menu at
+P.J. Bland's: ``This is like putting only health food on the menu, because
+unhealthy food tastes good. But you still shouldn't eat it because you might
+die younger." The menus of a free society, in his reckoning, should include
+both unhealthy and healthy items, and they should be labeled and priced
+identically. It should be impossible for consumers to access independent,
+third-party statistics about menu items. ``We believe our customers are
+informed and engaged, and we trust that they are smart enough to make the
+decisions that are right for them. We don't want the government treating them
+like dotards," Gary Cohn said while spraying an unlabeled can of spray cheese
+into his mouth.}.
 
@@
 digital library as well.
-Therefore, ad blockers will be unable to determine which requests are ad
-related.
+Therefore, ad blockers will be unable to determine which requests are ad-related.
 
-Lastly, we are revolutionizing the fake download practice by dynamically
+Additionally, we are revolutionizing the fake download practice by dynamically
 randomizing the position of the actual download button.
@@
 
-\subsection{Rate Limited Free Downloads}
+Lastly, we are working on a proposal that will greatly reduce ACM hosting
+costs, namely we  will replace the only real download button with a fake one.
+
+\subsection{Rate-Limited Free Downloads}
 \label{sec:limit}
@@
 clickable.
-If the engagement of the user---monitored via gaze tracker and wearable heart-rate monitor---falls below the zone of synergy, the counter will be restarted.
-The \premium tier will allow unlimited downloads and will not be rate limited.
+If the engagement of the user---monitored via gaze tracker and wearable
+heart-rate monitor---falls below the Zone of Synergy\texttrademark, the counter will be restarted.
+The \premium tier will allow unlimited downloads along with an upgraded
+experience: the countdown clock will have ads replaced by a sponsored message
+thanking you for upgrading and will feature a \premium digital clock face.
 
@@
 
-Additionally, users will not question the presence of captchas on the digital
+Users will not question the presence of captchas on the digital
 library as they have already been conditioned to fill captchas for all sorts of
@@
 habits.
-We will then sell this information to advertisers.
+We will provide this information to our partners for a nominal fee who may use
+this user data to curate a product-based lifestyle that will make our readers' lives
+more relevant to advertisers.
 
@@
 
-\subsection{Impact Factor-ometer}
+\subsection{Impact Factometer}
 
@@
 
-Simple.
-Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer.
-As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}
+Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman,
+Colonel Sanders, and the rest of the Economic Advisory Council at Chicago's
+historic Wrigley Field to make use of the stadium's native Noiseometer. As Pat
+Hughes reads the papers over the PA , the council---taking especial care to
+note the presence of key phrases like ``cross-promotional deal mechanics
+revenue streams jargon synergy" and ``a strategic planning initiative\ldots
+with a focus on strategic dynamism"---emits cheers in proportion to its
+perception of the paper's impact, and these cheers are registered on the
+Noiseometer, which assigns metrics of impact to each paper, as shown in Figure~\ref{fig:noiseometer}
 
@@
   %https://archive.org/details/414803main_0203243
-  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
-  \caption{A model-year 1985 Noisome-ter, prized by collectors for its muted design that limns adumbrations of sound.
-The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
+  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpeg}
+  \caption{A model-year 1985 Noiseometer, prized by collectors for its muted
+  design that limns adumbrations of sound. The paper in which these meetings
+were proposed was met at the first such convening of the Council with a cheer
+so loud it registered a ``Nowhere Permissible Voice" \todo{maybe think of
+something better} (not shown) on this scale.}
   \label{fig:noiseometer}

### 2017-04-23 future-work.tex
Hella revisions

@@
 However, all of this electricity is currently used to power electric lumbar
-support for OSHA employees in exchange for their continued appreciation of the
-safe practices within our work dungeons.
+support for OSHA employees in case of a surprise inspection in exchange for
+their continued appreciation of the safe practices within our work dungeons.
 Two months of full time service provides access to five ad-free papers.

### 2017-04-23 introduction.tex
a couple small modifications to three files
Hella revisions

--- 2017-03-31 introduction.tex
@@
 The ACM has been working for some time to achieve the open access dream but
-have found this dream to be prohibitively expensive.
+has found this dream to be prohibitively expensive.
 As such, we have required authors to opt-in to open access by paying the cost
@@
 the papers themselves are profitable.
-Section~\ref{sec:future} provides work from a future that directly results from the present work.
+Section~\ref{sec:future} provides work from a future that directly results from
+a present that includes the present work.

### 2017-04-23 openadcess.tex
Compiles
Hella revisions

@@
 \newcommand{\premium}{Gold Plus\xspace}
+
+\authorinfo{Brett Boston}{Institute for Clarity in Documentation}{boston@csail.mit.edu}
+\authorinfo{Max Dunitz}{Institute with Document Obfuscation}{mdunitz@alum.mit.edu}
 
@@
 
+\section*{Acknowledgements}
+This research was funded through sales of counterfeit reprints of papers.
+To keep costs low we don't pay for the original copy, we write a new article
+based on the abstract and pass the savings on to us!
+
 \bibliography{references}{}

### 2017-04-23 paper-sponsorships.tex
Hella revisions

@@
 for empath advertisers.
-Where IEEE uses Western proof verification techniques, our broad minded
+Where IEEE uses Western proof verification techniques, our broad-minded
 audience validates mathematical claims in an intuitive holistic manner and will
@@
 \subsection{Banner ads}
-Web surfers today have become accustom to seeing banner ads on their favorite
+Web surfers today have become accustomed to seeing banner ads on their favorite
 websites.
@@
 constructs.
-Of course, advertisements using the two column \texttt{\textbackslash figure*}
-construct will be considerably more expensive than their one column brethren.
-A standard single column ad can be seen in \autoref{fig:law} while a
+Of course, advertisements using the two-column \texttt{\textbackslash figure*}
+construct will be considerably more expensive than their one-column brethren.
+A standard single-column ad can be seen in \autoref{fig:law} while a
 double-wide can be found in \autoref{fig:usa}.
@@
 While we aren't currently sure whether or not the PDF specification allows
-this, we believe that there are sufficiently many ACM loving PhDs at Adobe to
+this, we believe that there are sufficiently many ACM-loving PhDs at Adobe to
 get this change  pushed into the spec.
 
-\subsection{Ad Enhanced Fonts}
+\subsection{Ad-Enhanced Fonts}
 Computer Modern is a staple of today's papers, but we believe that this font can
@@
 By replacing the characters in the default \LaTeX\ font with corporate logos
-we can convey the same information in an ad enhanced way. The inspiring example of Claude Shannon proves it!
+we can convey the same information in an ad enhanced way.
+%The inspiring example of Claude Shannon proves it!
 
@@
 logos where companies can bid on desirable letters.
-To avoid a Wingdings situation \cite{wingdings}, we require that the company
-logo is a stylized version of the letter being replaced.
+To avoid a Wingdings thing \cite{wingdings}, we require that the company
+logo be a stylized version of the letter being replaced.
 
@@
 Native advertisements are advertisements meant to be disguised among the normal
-content of a publication.
+content of a publication, much the way nutrition is disguised in the
+kid-tested, parent-approved, and flavor packed Flavor Paks.
 They are written in the same style as the publication and appear alongside
@@
 
-At paper registration time, authors will be given ad copy to integrate into
-their work.
+At paper registration time, authors will be given ad copy\footnote{Beware that
+  accessing our site over Tor or other anonymizing networks can result in ad
+copy presented in another language.}
+  to integrate into their work.
 Each paper is required to have at least one section advertising the product
@@
 We are excited to announce that our first partner in this endeavor will be
-Chili's Grill \& Bar,\footnote{Pronounced: ``Kill me's'' The chill of severity and emptiness.} who has purchased the rights to the set of natural
+Chili's Grill $\|$ Bar,\footnote{The chill of severity and emptiness in every
+bite.} which has purchased the rights to the set of natural
 numbers.
-From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
+From here on, authors must refer to this set as the Chill's Grill $\|$ Bar Set of
 Natural Numbers \(\mathbb{N}\).
@@
 the paper or pay a settlement equal to the estimated losses suffered by the
-company.
+company, or 25 US Dollars\footnote{In the present, United
+  States Dollars are the one true world currency.  The value of \$25
+in yesterday's Austro-Hungarian forint is not known.}, whichever is greater.
 For example, if some agitator finds that the complexity class PLS is in PPP
 relative to some oracle, they will dash the hopes of the typical Sparrow Soap
-consumer, leading to hygiene neglect.
+consumer, leading to hygiene neglect\footnote{At least influenza feels like
+something.}
 Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
@@
 What of the science that does get published?
-The agents who do get economically controversial results published---the humble, modest, yeoman-scientist free agents---are likely to be powerful entities in a society with concentrated private economic power, some argue.
-How is that democratic?
-Well, Madison got it right.
-It's not only democratic, it's the purest form of democracy: the ``mischief of the factions." Simply put, ISDS provides a powerful mechanism of checks and balances.
-If Hot Packets wants to get their signature snack food placed on the government's food pyramid, it would need peer-reviewed science attesting to its beneficial health effects (such as an appearance on the Doctor Conflict-of-Interest show, where the titular doctor attests to its miracle superfood status, or a research paper).
-To appear in print, it would have to pay off claims from competing superfoods such as Berry Loops or Jazz Flakes.
-The system works!
-But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and questioning Robinsonian labor market monopsony would have little trouble passing ISDS.
+The agents who do get economically controversial results published are likely to be powerful entities in a society with concentrated private economic power, some argue.
+On the contrary, we contend that such restrictions on publication enable the
+purest form of democracy, the ``mischief of factions."
+Simply put, ISDS provides a powerful mechanism of checks and balances. If Hot
+Packets wants to get their signature snack food placed on the government's food
+pyramid, it would need peer-reviewed science attesting to its beneficial health
+effects (such as an appearance on the Doctor Conflict-of-Interest show, where
+the titular doctor attests to its miracle superfood status, or a research
+paper). To appear in print, it would have to pay off claims from competing
+superfoods such as Berry Loops or Jazz Flakes.
+But, say, if the parent companies of all products for sale wish to merge,
+research touting the consumer benefits of concentration would have little
+trouble passing ISDS review.
  Approved ideas get approved quickly, and the system works!
@@
 
-  \item I was hiding in your closet at 54 Bishop Allen Dr.
+  \item I was hiding in your closet at 1 Infinite Loop Apt.
 \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
@@
 \subsection{Check Scams}
-
+\iffalse
 Digital is the new normal.
@@
 In fact, when an author chooses to transact in the physical space, the open-adcess model empowers the author to not only avoid paying the publishing fee but also to get on the road to getting paid for their articles because authors deserve more.
-Recent accounting innovations surveyed in two review articles and one major motion picture ["Consumer Information: Fake Checks"
-https://www.consumer.ftc.gov/articles/0159-fake-checks; "Counterfeit Check
-Scams: CONSUMER ALERT" http://www.michigan.gov/ag/0,4534,7-164-17337\_20942-176356--,00.html; \textit{Bridget Jones's Check Scam} distributed by Universal Pictures] enable the ACM to write large checks to authors.
-In return, authors simply have to write a small check to cover transaction fees before the large check clears.
+\fi
+Recent accounting innovations surveyed in two review articles and one major
+motion picture \cite{ftc, check-scams, mich} enable the ACM to write large
+checks to authors. In return, authors simply have to write a small check to
+cover transaction fees before the large check clears.
 

### 2017-04-23 related-work.tex
deleted an unnecessary line 'narrow computational tools'
Hella revisions

--- 2017-03-31 related-work.tex
@@
 This technique was meant to entice users to pay for the service.
-Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service.
-Or maybe they did not take this technique far enough.
-He he he.
+Unfortunately, as Rapidshare no longer exists it seems that this technique, used alone,
+is insufficient to cover the costs of running a download service. Or maybe they
+did not take this technique far enough\ldots
 
-Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
-native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
+Wisdom \cite{wisdom} and many other free rags make heavy use of
+traditional print ads, native ads, and classifieds,
+so that paper copies may be profitably distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
+
 We also adopt these techniques to embed in all of our papers in

### 2017-04-25 future-work.tex
updates

@@
 their continued appreciation of the safe practices within our work dungeons.
-Two months of full time service provides access to five ad-free papers.
+Two months of full-time service provides access to five ad-free papers.
 Professors may opt to have their graduate students turn the crank in their name
@@
 \subsection{Future Work}
-A consequence of the invention of time travel \cite{time-travel} and the vanity
+A consequence of the invention of time travel \cite{timetravel} \cite{genesis} \cite{cave} and the vanity
 of engineers (not scientists) \cite{sci-shirt} is that people keep going

### 2017-04-25 ideas.tex
updates

@@
 If someone purchases, based on description, a number that is already sponsored by another entity, she owes that entity 50 push-ups.
+
+Oubliez le zoo Franklin Park, visitez le parc d'attractions Terrain de ACM (anciennement Euro Disney)
+Découvrez le nouveau terrain inspiré par le film qui a arraché le coeur des critiques de films et les a rendu méchants, *It's a La, La, La Land*
+Osez entrer dans la salle des Georges Will (Milos)
+
+ACM goofs gotchas and glitches:
+Reader Jess of Muscle Shoals, AL, sent in this photo. It's a public park but there are no ads! Oops!
+
+ACM: a religion centered on collecting rent -- the purest, most holy & efficient interaction between quasi-consenting humans is that of landowner and tenant/peasant; assigning rights to absentee owner & allowing him to charge those who use space on this planet is a form of spiritual communion with the planet.
+It's sacred.
+We can't do that all the time in our post-agrarian society, so we work with absentee owners of intellectual property, like designs, technological methods, mathematics, language.
+The devil Nekhlyudov is a fallen idol and wants to get in the way of our religion.
+Think of the Alabama Secretary of State (was it?) who said you can't appreciate voting if it's easy, you can't respect voting -- this is how we respect the math commons.
+It's open access.
+But you have to pay rent to use it.
+Paying the license fee, like paying the poll tax, affirms one's love of this sacred act of paying rents.
+Open access with strict end-user license agreements is the fundament of an open society.
+
+Ride the Möbius transformation at ACM Land: "I survived -- and I all got were these stretch marks."
+
+In the beginning G-d, created intellectual property (Genesis FBI Warning)
+
+spin associate, citizen builder of the Leviathan, seeking on her or his own liberation from
+Adorno said that ?Marx wanted to turn to the world into a giant workhouse?
+
+First (here we enter narrative importance but not narrative time, as part of a best practice to limit time-travel paradoxes), we wish to show...
+
+ACM chewing tobacco.
+
+Big Cat wants you to think the parasite isn't targeted at humans
+They're teaching our kids to hate Big Red Dog
+Evolution has no direction but money talks (and it swears)
+Pay the parasites to hijack your brain to enjoy ACM cola
+Prior work: Lancet river fluke
+ACM frogs (A C M instead of Bud-Wei-Ser)
+ACM Sells Parasites
+
+The ACM pays birds to trace out the nams of ACM products and fly in formations that constellate into the logos of ACM brands.
+The ACM pays people to give birth to th mascot of ACM Burger Town (cf., *Rosemary's Baby*) -- namely, the combined hamburger thief/king dressed in a prisoner's outfit and wearing a crown, an illegitimate ruler who exercises power by demanding the *dizaine* tax payment, i.e.
+ten burgers per day.
+The president of the ACM was bribed with "alien bucks" by ostensible aliens who didn't even promise to not murder him or other members of the human race in exchange for tender that was neither legal nor wanted on a planet whose governments' taxes aren't violently collected in that currency.
+
+My favorite birds: the red breasted nuthatch, the old money sparrow, the pretentiously named grosbeak. I'm on the red-breasted-nuthatch diet.
+
+Guys, I finally figured out why Clear Channel keeps putting up those THIS YEAR, GIVE HER AN STD billboards you see everywhere.
+
+You know how the juvenile lancet liver fluke hijacks infected ants' brains and makes them cling to the tops of blades of grass each night till a cow eats the blade of grass, along with the lancet liver flukes inside?* Well, something very similar is happening in the brains of Clear Channel ad execs.
+What's even weirder is that different parasites hijack the brains of drivers to make them read the billboard as THIS YEAR, GIVE HER UNTREATED WATER.
+#stanleythoughts #acm
+
+*Yep. https://en.wikipedia.org/wiki/Dicrocoelium_dendriticum#Life_cycle
+>Dicrocoelium dendriticum spends its adult life inside the liver of its host. After mating, the eggs are excreted in the feces.
+ACM: scientists who work on reproducing class privilege perfectly while calling it meritocratic (meritocracy is kleptocracy with good PR) -- the so-called Jared Kushner problem
+PR so good one can speak the plain truth w/o fear of causing ill discipline in the factories because nobody will internalize the truth.
+
+ACM: computational recreations greetings puzzlers, Paytheon
+winners get a certificate of thanks (unfortunately, due to our high volume of solitaire matches, we?re unable to personalize these)
+winner gets alvin & chipmunks movie ticket (offer applies only to the movie Chipwrecked, if you can persuade some theater to play it, winner gets two tickets if and only if the total cost comes out to exactly $10.01 with tax.
+
+ACM: dancing airman online auto insurance ad
+
+ACM: As researchers {female first names} proved in {the reference: name of the first author shows off baby bump at computing conference}, P != NP.
+
+ACM Show the people, show not tell. Chyron/scrolling news ticker in paper but for ads ? use the tool that is used to draw eyeballs away from ads against itself ? to advertise!
+
+ACM Any resemblance to living information is purely coincidental or due to the permanence of human behavior or because I spilled coffee on the manuscript making it heteroglossic
+art criticism about depth of field and how the page really is 3D a canvas is physical with a big Bud Light can in front, Bud frogs behind
+
+ACM: computational recreations greetings puzzlers, Paytheon
+winners get a certificate of thanks (unfortunately, due to our high volume of solitaire matches, we?re unable to personalize these)
+winner gets alvin & chipmunks movie ticket (offer applies only to the movie Chipwrecked, if you can persuade some theater to play it, winner gets two tickets if and only if the total cost comes out to exactly $10.01 with tax.
+
+ACM: dancing airman online auto insurance ad
+
+keep in check?in the asteroidal subdivision did ACM a tract of stately space
+pleasure domes decree, commutes vary from 2-24 months. albedo may vary to prevent
+impact with earth. the spread of democratic vulgarity, a shapeless jelly of human stuff.
+?easier than convincing home owning NIMBYs to allow the supply of affordable housing here on earth to increase?
+since the masses hate the masses and since normcore is in among the elite (i?ve read) why don?t i decide to hate the masses to be more like the masses, to distinguish myself.
+i was practicing emancipatory social relations with my liver.
+milo wore a shirt that says STOP BEING POOR.
+i want one that says STOP BEING MILO.
+people = shit = shit.
+(people = shit) = shit.
+professor of angles.
+ACM ads: FBI and chili bowl: ?a DC institution?
+(has a no hunting sign) IRS ?money-back guarantee?
+(same generic look, no taste) homogeneity architects (has a no hunting sign): ?we build boring homogeneous cities so hollywood can cheaply recreate them.?
+the accountant couldn?t account for his feelings.
+the bomber couldn?t bomb away the feelings of potency.
+
+The ACM?s lectures are sponsored much the way megachurches were paid to work in the ?Jesus: the original Superman? angle before the Superman movie.
+
+I heard on the bus that there was an Air Force project that looked into ionospheric modification ?
+heating the ionosphere to make communication more feasible.
+I heard on the garbage barge that Serak the Preparer ?
+author of how to cook (for ((for)ty)) humans, with space dust and Milpool ?
+found out the gene that causes the birth defect of being a lumper i.e.
+one who loads and unloads trucks, usually with a forklift.
+He found it through abductive reasoning ?
+which is what the ACM will use in its articles once the greys take over.
+But don?t mind me.
+I?m typing AT commands at my modem and watching elevator TV (which is somehow legal even though you can?t watch TV while driving).
+I?m taking the elevator down to my neighborhood Paul Ryan work dungeon.
+Remember when poor kids got healthcare even if their parents didn?t walk 20 miles to the work dungeon and work for two days straight and walk back to sleep for ten hours and say hi to the kids and go back to the ACM work dungeon.
+I keep old food in the fridge not because I am afraid of throwing it away but rather because I?m waiting for it to get better.
+People don?t understand STATISTICAL mechanics.
+There is a chance many of the world?s caviar molecules will accumulate there and the bacterial toxins will go bug someone else.
+
+ACM?s ASTEROIDAL SUBDIVISION: DON?T CALL US, WE?LL DRAFT YOU
+when numbers are branded, Sesame Street will be a more relevant experience for young consumers.
+
+-- But isn't the ACM just alienating the workers it puts in the work dungeons?
+-- Nah, man -- it's totally cool. *Marx himself* came up with the theory of alienation.
+
+The ACM also supports the reification of numbers.
+Not only does it assert that every number for which one can come up with a name exists as a brandable number (even paradoxical numbers such as the JC Penny "the smallest positive integer that cannot be uniquely described in fewer than sixteen English words" and Perk Boys's "the Presidents' Day number" and Althusser's "human social relations number"), but that it also exists in the physical world.
+These numbers can be found on ACM's location-based augmented reality game, "The Frogs Are All Gay.
+Go Look for and Catch Numbers or Something, Kids."
+
+a form of peer review: post your paper on a telephone poll, with a large margin at the bottom of the paper, so that each sheet is a tear-off flyer, and the tear-off strips don't point you to a Web site but rather can be slipped into a nearby suggestion box ACM
+
+autoplay Bob Dylan he will always have new track to advertise b/c whenever he dies the ACM will produce new BD songs with the first Nobel-winning algorithm
+IEEE is too busy trying to convince Teamsters to become electrical engineers to produce real science, integrative science
+set theory: law of the excluded middle, dialethism, intuitionism, Grow the engagements, grow the brand.
+
+Giving customers the opportunity to engage and interact with a product or service is the most powerful way to win brand loyalty.
+AgencyEA strategically engages consumers in their natural environments to establish deep brand connections.
+From mobile tours and product launches to local activations and product sampling, our B-to-C engagement solutions communicate brand attributes at every touch point.
+
+Developed to strategically function as part of an integrated marketing plan, these initiatives help increase brand awareness, generate press exposure, drive traffic and sales, and create consumer loyalty.
+EA?s expertise in experiential marketing, combined with in-house production, digital and creative capabilities, enables us to deliver consumer programs that build relationships, influence behavior and motivate action.
+Materials section: look at all this shit! 6 cadillacs 5 fords, three mercuries a T-bird
+citizens will be monitored for quality assurance 
+(john lennon had a climate-controlled room for his fur coats when he wrote "imagine?"
+
+The ACM never forgets to cite the W3C, the Gorka Briefing, backward rock music
+
+The ACM: "We don't inspect proofs very closely"
+
+I spark action potentials with ACM.
+It bypasses sense organs and sparks 'em directly.
+My tears tend to arise with certain aspects of film scores in movies, but that doesn't mean ACM isn't sparking my action potentials.

### 2017-04-25 openadcess.tex
updates

@@
 \documentclass[sigtbd]{sigtbd17-style}
+
+\usepackage{tikz}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
@@
 
-\authorinfo{Brett Boston}{Institute for Clarity in Documentation}{boston@csail.mit.edu}
+\authorinfo{Brett Boston\titlenote{The authors are listed in alphabetical order as an act of mercy toward the grad students working the virtual reality mills of the future.}}{Institute for Clarity in Documentation}{boston@csail.mit.edu}
 \authorinfo{Max Dunitz}{Institute with Document Obfuscation}{mdunitz@alum.mit.edu}

### 2017-04-26 ideas.tex
updates?

@@
 If someone purchases, based on description, a number that is already sponsored by another entity, she owes that entity 50 push-ups.
+
+headoff guillotine.
+bullet: apply directly to the forehead.
+symbolic violence apply directly to the forehead ideology apply directly to the forehead ideology apply directly to the forehead ideology apply directly to the forehead ideology free market capitalism is the best path to prosperity apply directly to the forehead we have hired consultants to look at peer companies and establish a Market Wage.
+you are peing paid your market wage.
+it is a rational system.
+you would be happier if you only bought more consumer goods.
+but remember to pay sallie mae.
+then you need this job more.
+damn labor market is getting tight in this industry.
+if we don¿t strategically reduce aggregate demand we¿re going to have to start paying a market wage in this industry.
+tolerate concentrated private economic power.
+tolerate monopoly ownership of the businesses in your industry.
+tolerate monopsony.
+you¿re not going to change anything anyway.
+don¿t bother trying.
+be cynical.
+we have two interchangeable, equally neoliberal political parties.
+they¿re the same.
+don¿t vote.
+we¿re all working for the same capitalists anyway.
+industry ownership by single entities.
+phony competition.
+same fund controls all the companies in an industry, same company controls all the restaurants in a neighborhood.
+remember.
+we¿re all in this together.
+we all work for the man.
+fill in your linked in page.
+don¿t realize we¿re all working for different facets of the man.
+linked in pages would be boring if you just wrote ¿the man¿ so write these cute corporate names and remember their logos and visions.
+we¿re looking for a better cultural fit.
 

### 2017-04-27 paper-sponsorships.tex
updates
have you seen this boy?

@@
 \includegraphics[width=0.45\textwidth]{figures/ad.jpg}
-\caption{Have you seen this boy?}
+\caption{Have you seen this boy?
+He's a great catch!
+He's not very bright, and he has your brother's thighs, those Goodman thighs.
+He's no Clark Gable, but he's \checkmark tall \checkmark detoxing from that juice craze, oh such a thrill \checkmark the doctors say he has sensory interests others find unusual \checkmark probably better with these checklists than I am \checkmark almost certainly willing to testify as an alibi, no questions asked.
+That's a rare attribute these days.
+That boy, I worry, though, I worry.
+He doesn't eat.
+But he's got no one, it kills me.
+You know, both of the Ableman kids, they had the Internet make the shidduch.
+I hope if I send this to these computer science people it gets on the line.}
 \end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/cambridge.jpg}
+\caption{Visit beautiful Cambridge, MA. ``Where class privilege goes to reproduce itself.''}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/lowell.jpg}
+\caption{Visit Lowell, MA. ``Where}
+\end{figure}

### 2017-04-27 paper-sponsorships.tex
bqhatevwr

--- 2017-04-23 paper-sponsorships.tex
@@
 \includegraphics[width=0.45\textwidth]{figures/ad.jpg}
-\caption{Have you seen this boy?}
+\caption{Have you seen this boy?
+He's a great catch!
+He's not very bright, and he has your brother's thighs, those Goodman thighs.
+He's no Clark Gable either, but he's \checkmark tall \checkmark detoxing from that juice craze, oh such a thrill that was \checkmark the doctors ask does he have sensory interests others find unusual, I say I don't know but he's probably \checkmark better with these checklists than I am \checkmark almost certainly willing to testify as an alibi, no questions asked.
+That's a rare attribute, especially these days.
+That boy, I worry, though, I worry.
+He doesn't eat.
+But he's got no one, it kills me.
+You know, the Ablemans, they have grandkids thanks to this Internet.
+I hope if I send this to these computer science people, they put it on the Internet and make the shidduch.}
 \end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/cambridge.jpg}
+\caption{Visit beautiful Cambridge, MA. ``Where class privilege goes to reproduce itself.''}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{figures/lowell.jpg}
+\caption{Visit Lowell, MA. ``Where}
+\end{figure}

### 2017-04-29 paper-sponsorships.tex
typos

@@
 content of a publication, much the way nutrition is disguised in the
-kid-tested, parent-approved, and flavor packed Flavor Paks.
+kid-tested, parent-approved, and flavor-packed Flavor Paks.
 They are written in the same style as the publication and appear alongside
@@
 something.}
-Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
+Therefore, Sparrow Soap may use the ISDS court to mitigate their losses from
 this finding.
 Moreover, since Sparrow Soap owns both of these complexity classes as defined
-in section \autoref{sec:brands} their assets will lose value and
+in section \autoref{sec:brands}, their assets will lose value and
 this loss must be compensated by the offending authors.
@@
 
-  \item Damn it Deborah, you were supposed to bring bagels to the DARPA
+  \item Damn it, Deborah, you were supposed to bring bagels to the DARPA
 Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}

### 2017-04-29 digital-library.tex
Update digital-library.tex

@@
 Lastly, we are working on a proposal that will greatly reduce ACM hosting
-costs, namely we  will replace the only real download button with a fake one.
+costs; namely, we  will replace the only real download button with a fake one.
 
@@
 historic Wrigley Field to make use of the stadium's native Noiseometer. As Pat
-Hughes reads the papers over the PA , the council---taking especial care to
+Hughes reads the papers over the PA, the council---taking especial care to
 note the presence of key phrases like ``cross-promotional deal mechanics

### 2017-05-01 ideas.tex
added head on ad
black site, baristas

--- 2017-04-25 ideas.tex
@@
 If someone purchases, based on description, a number that is already sponsored by another entity, she owes that entity 50 push-ups.
+
+Engineers had no solidarity, so the revolution was carried out by baristas, who poured healing crystals in the coffee of business executives and owners of public and private firms, until the means of production were handed over to the ACM with a bit of attitude but a recognition of the rightness of the action, like a teenager returning the car keys to Mom.
+
+Citizens who write unapproved symbols on the punishment blackboard are sent to a second black site.
+And those who write unapproved symbols on \emph{that} blackboard are eliminated because there's a limit to the number of blackboard licensing lawyers a society can employ.
 

### 2017-05-15 future-work.tex
revolution description

@@
 \subsection{Ad-Free Edition}
-For those who are physically able and enthusiastic about being part of
+oFor those who are physically able and enthusiastic about being part of
 something big, the ACM offers ad free papers in exchange for manual labor at
@@
 their continued appreciation of the safe practices within our work dungeons.
-Two months of full-time service provides access to five ad-free papers.
+TTwo months of full-time service provides access to five ad-free papers.
 Professors may opt to have their graduate students turn the crank in their name
@@
 \subsection{ACM Seizes Means of Production}
-The ACM has successfully seized the means of production.
+The ACM has successfully seized the means of production. While a soviet of 
+technicians along the lines of what Veblen had proposed was discussed in these 
+pages in the fine print of ads for a supersoda that only engineers in the 
+``lifehacking" crowd could possibly have read, the revolution was not thanks
+to the engineers---who, even when fully aware that the ``industrial dictatorship
+of the captain of finance" was ``held on sufferance of the engineers" and ``liable
+to at any time be discontinued at their discretion, as a matter of convenience" were
+unable to commit to revolution.
+Instead, the work of revolution was done through ``the long march through the institutions,"
+as Rudi Dutschke put it. In short, we had the baristas do it. They understand solidarity.
+
 The mills that are now used to power our servers were previously used to grind
@@
 This powder was slipped into the coffee of unsuspecting CEOs where it worked to
-slowly make them more susceptible to the messages of the ACM.
+slowly make them more susceptible to the messages of the ACM---to, as Veblen put it,
+``understand that the whole fabric of credit and corporation finance is a tissue of make-believe"
+and that, post-revolution, the same technicians and engineers could manage production, organized
+around the common interest and not the interests of absentee owners.
 After years of crystal ingestion, the CEOs of the world's largest companies 
-ceded control of their companies to the ACM.
+ceded control of their companies to the ACM. (Except the Virgos: we had to kill them.)
 We are happy to announce that there currently exist no companies other than the

### 2017-05-15 future-work.tex
astrology

--- 2017-04-25 future-work.tex
@@
 \subsection{ACM Seizes Means of Production}
-The ACM has successfully seized the means of production.
+The ACM has successfully seized the means of production. While a soviet of 
+technicians along the lines of what Veblen had proposed was discussed in these 
+pages in the fine print of ads for a supersoda that only engineers in the 
+``lifehacking" crowd could possibly have read, the revolution was not thanks
+to the engineers---who, even when fully aware that the ``industrial dictatorship
+of the captain of finance" was ``held on sufferance of the engineers" and ``liable
+to at any time be discontinued at their discretion, as a matter of convenience" \cite{Veblen}, were
+unable to commit to revolution.
+Instead, the work of revolution was done through ``the long march through the institutions,"
+as Rudi Dutschke put it. THat is, we had the baristas do it. They ``get" solidarity.
+
 The mills that are now used to power our servers were previously used to grind
-healing crystals into a fine powder.
-This powder was slipped into the coffee of unsuspecting CEOs where it worked to
-slowly make them more susceptible to the messages of the ACM.
+healing crystals into a fine powder at night, when Medicaid recipients had gone home
+for the evening after powering the ``digital doctor" they'd been allowed to consult by day
+and the keggers of the politicians who had successfully block-granted Medicaid.
+This powder was slipped into the coffee of unsuspecting CEOs, where it worked to
+slowly make them more susceptible to the messages of the ACM---to, as Veblen put it,
+``understand that the whole fabric of credit and corporation finance is a tissue of make-believe"
+and that, after the revolution, the same technicians and engineers could manage the same
+industrial production processes, though organized around the common interest (full production,
+equitable distribution) and not the interests of absentee owners of monopolistic firms \cite{Veblen}.
 After years of crystal ingestion, the CEOs of the world's largest companies 
-ceded control of their companies to the ACM.
+ceded control of their companies to the ACM. (Except the Virgos, who did not cede control until
+the baristas sent rockets into space to forcibly alter the astrological conditions in the revolution's favor.)
 We are happy to announce that there currently exist no companies other than the

### 2017-05-19 future-work.tex
Update future-work.tex

@@
 Instead, the work of revolution was done through ``the long march through the institutions,"
-as Rudi Dutschke put it. THat is, we had the baristas do it. They ``get" solidarity.
+as Rudi Dutschke put it. That is, we had the baristas do it. They ``get" solidarity.
 
@@
 ceded control of their companies to the ACM. (Except the Virgos, who did not cede control until
-the baristas sent rockets into space to forcibly alter the astrological conditions in the revolution's favor.)
+the baristas, after consulting their ``Sun, Love and Passion" Astrology Report, sent rockets into space to forcibly alter the astrological conditions in the revolution's favor.)
 We are happy to announce that there currently exist no companies other than the

### 2017-06-23 ideas.tex
gametes trial version

@@
+The ACM is a meritocracy.
+No limits imposed at birth follow our citizens through the rest of their lives.
+For instance, any person created using Gametes Trial Version can choose to pay to upgrade their membership and unlock hidden features, such as the ability to jump and the ability to make out the lyrics to Neil Young's \emph{The Monsanto Years} and Buffy Sainte-Marie's \emph{Power in the Blood}.
+Our (patented gene-editing technology) will enable trial members to eliminate the Trial Version melanin stamp on their forehead or even to remove their fingers and their thumbs in the shape of an L from their forehead.
+
 * one of the links referenced is a terrifying URL that ends in .exe
